---
title: MetaCheck Report
subtitle: "Serotonin and Social Norms: Tryptophan Depletion Impairs Social Comparison and Leads to Resource Depletion in a Multiplayer Harvesting Game"
metacheck:
  version: "0.3.1 (pytacheck 0.3.1.dev1)"
  report-created: "2026-09-25"
format:
  html:
    theme: 
      light: flatly
      dark: darkly
    respect-user-color-scheme: true
    toc: true
    toc-title: >
      <ul class="emoji-key">
        <li class="red">⚠️ possible problems detected;</li> 
        <li class="yellow">🔍 something to check;</li> 
        <li class="green">✅️ no problems detected;</li>  
        <li class="info">ℹ️ informational only;</li>  
        <li class="na">⬜ not applicable;</li>  
        <li class="fail">☠️ check failed</li>
      <ul>
      <hr/>
      **Table of Contents**
    toc-location: right
    toc-expand: 3
    page-layout: full
    title-block-banner: "#15342A"    #"#327118"
    title-block-banner-color: "white"
    link-external-newwindow: true
    embed-resources: true
    format-links: false
    smooth-scroll: true
execute: 
  echo: false
  error: true
---

<style>
  #TOC * { border-left: none; }
  #TOC > ul { border-left: 1px solid #15342A; }
  #TOC > ul > li > ul > li { text-indent: -1.2em; margin-left: 1.2em; }
  main h2, main h3 { margin-left: -20px; }
  main h2 { font-size: 150%; font-face: italics; }
  main h3 { font-size: 125%; }
  main h4 { font-size: 110%; }
  .emoji-key li { margin-bottom: 0.5em; }
  section::before { content: '' !important; }
  th { background-color: #555; color: white; }
  table.dataTable, .dataTables_scrollBody { margin: 0.5em 0; }
  #info { position: absolute; top: 2.5em; right: 2.5em; color: white; }
  #info a { color: white !important; }
  .quarto-dark tr.even { background-color: #333; }
  .quarto-dark tr.odd { background-color: #222; }
  .quarto-dark div.datatables { color: white; }
  .quarto-dark table.dataTable { border: 1px solid #555; }
  table strong { color: red; }
  .quarto-dark table strong { color: yellow; }
  summary { color: #333; }
  .quarto-dark summary { color: #CCC; }
  .validation { display: block; 
                border: 2px solid #15342A; 
                border-radius: 1em; 
                padding: 0.5em 1em 0; 
                margin-bottom: 0.5em;
                background-color: #15342A33;}
</style>

::: {#info}
[MetaCheck](http://www.scienceverse.org/metacheck) version {{< meta metacheck.version >}}  
Report Created: {{< meta metacheck.report-created >}}  
DOI: [10.1177/0956797614527830](https://doi.org/10.1177/0956797614527830) <!-- doi, if exists -->
:::

[Metacheck](https://www.scienceverse.org/metacheck/) is a tool that screens scientific manuscripts and aims to identify potential issues for improvement. Our goal is to guide researchers towards best practices, especially with respect to practices that researchers easily forget, or might not have learned about yet. Metacheck is developed to help researchers correctly and completely report statistical results, will point to possibly relevant information about citations, and provides feedback about data and code sharing.

Metacheck combines existing and new checks in a module-based tool. It is open source, and anyone can contribute modules. It mainly relies on text search or retrieving information from external sources through API’s or web-scraping, but the power modules can optionally use large language models. The use of LLM's is always optional and opt-in. The development of Metacheck is guided by our [values statement](https://www.scienceverse.org/metacheck/#our-values).

::: {.validation}
In light with our values, our modules are validated on sets of open-access papers. In each validated module, there will be a sentence explaining the prevalence of false positives (incorrect detection/classification) and false negatives (incorrect omission). For example, if a hypothetical module detects the inappropriate practice of "woozling", the sentence might read:

> In a sample of 250 papers from the *Journal of X*, there were 350 instances of woozling. This module correctly detected 340 of them, and incorrectly identified 7. Therefore 3% of true instances are missed, and 2% of detections are false positives.

There is an inherent tradeoff between false positives and false negatives. Many of our modules are designed like "smoke detectors", where they are more likely to detect a practice that needs attention, but also more likely to incorrectly flag something. Therefore, you need to check the output of each module, keeping the validated error rates in mind.
:::

Metacheck is under continuous development. It can be surprisingly difficult to automatically retrieve information from papers, and there is a large amount of edge-cases where our tool might not yet work accurately. By using our tool, and providing us with feedback about what we can't get right yet, you will help to improve the tool for all other users. Issues can be submitted [on Github](https://github.com/scienceverse/metacheck/issues), and suggestions for improvement or feedback can be sent to [metacheck@scienceverse.org](mailto:metacheck@scienceverse.org).


## Summary

- ✅️ [Funding Check](#funding-check){.green}: A funding statement was detected.  
- ✅️ [COI Check](#coi-check){.green}: A conflict of interest statement was detected.  
- ℹ️ [List All URLs](#list-all-urls){.info}:   
- 🔍 [Open Practices Check](#open-practices-check){.yellow}: Shared data detected.  
- ✅️ [Ethics Approval Check](#ethics-approval-check){.green}: All papers that appeared to involve live data collection contained an ethics approval statement.  
- ✅️ [Funding Check (Overinclusive)](#funding-check-(overinclusive)){.green}: A funding statement was detected.  
- ✅️ [COI Check Overinclusive](#coi-check-overinclusive){.green}: A conflict of interest statement was detected.  
- ⬜ [Preregistration Check](#preregistration-check){.na}: No preregistration links were found.  
- ⬜ [Power Analysis Check](#power-analysis-check){.na}: No power analyses were detected.  
- ⬜ [Repository Check](#repository-check){.na}: We found no links to repositories on the Open Science Framework, Github, ResearchBox, DSpace, Zenodo, Dataverse, Figshare, Dryad, ReShare, 4TU.ResearchData, Mendeley Data, or DataONE.  
- ⬜ [Code Check](#code-check){.na}: We found 0 R, 0 Python, 0 SAS, 0 SPSS, 0 Stata, 0 Mplus, 0 MATLAB, and 0 JASP code files.  
- ⬜ [StatCheck](#statcheck){.na}: No detectable t- or F-tests. StatCheck currently only detects statistics written in APA format.  
- ⚠️ [Exact P-Values](#exact-p-values){.red}: We found 2 imprecise *p* values out of 13 detected *p* values.  
- ✅️ [Non-Significant P Value Check](#non-significant-p-value-check){.green}: We detected no nonsignificant p values.  
- ⬜ [Effect Sizes in t-tests and F-tests](#effect-sizes-in-t-tests-and-f-tests){.na}: No t-tests or F-tests were detected.  
- ✅️ [Marginal Significance](#marginal-significance){.green}: You described 0 effects with terms related to 'marginally significant'.  
- ℹ️ [List All P-Values](#list-all-p-values){.info}: We found 13 p-values  
- ⬜ [Data Check](#data-check){.na}: We found no files to analyse.  
- ⬜ [Codebook Check](#codebook-check){.na}: We found no extracted data columns to check against a codebook.  
- ⬜ [Psych-DS Check](#psych-ds-check){.na}: We found no repository files to check for Psych-DS compliance.  
- ⬜ [Reproducibility Check](#reproducibility-check){.na}: 
    -  We found no R code files to assess for reproducibility.  
- ✅️ [Reference Accuracy](#reference-accuracy){.green}: We checked the 0 references that supplied a DOI against the record that DOI points to, and found 0 incoherent references to check for parsing errors or mistakes. 7 references had no DOI and could not be checked. Incoherent references are mostly PDF parsing errors (we are working on improving reference parsing). Adding a DOI to every reference that has one lets the other reference checks (retraction, PubPeer, and replication) run on them too.  
- ⬜ [Replication Check](#replication-check){.na}: No citations to articles in the FLoRA database were found.  
- ⬜ [RetractionWatch](#retractionwatch){.na}: No citations to articles in the RetractionWatch database were found.  
- ℹ️ [Summarise References](#summarise-references){.info}: Summary information provided for 38 references  
- ⚠️ [Reference Consistency](#reference-consistency){.red}: There are cross-references that are not in the bibliography and/or bibliography entries not cross-referenced in the text  
- ✅️ [Miscitation](#miscitation){.green}: We detected no miscited papers  
- ☠️ [ref_pubpeer](#ref_pubpeer){.fail}: This module failed to run  



## General Modules

### ✅️ Funding Check {#funding-check .green}

A funding statement was detected.

<details><summary>View detailed feedback</summary><div>

The following funding statement was detected:

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("This work was supported by the Medical Research Council (Grant No. G0700410) and the Economic and Social Research Council (Grant No. ES/K002201/1)."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract funding statements.

The Funding Check module uses regular expressions to check sentences for words related to funding statements. It will return the sentences in which the conflict of interest statement was found.

The function incorporates code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This module was developed by Daniel Lakens

:::

### ✅️ COI Check {#coi-check .green}

A conflict of interest statement was detected.

<details><summary>View detailed feedback</summary><div>

The following conflict of interest statement was detected.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("The authors declared that they had no conflicts of interest with respect to their authorship or the publication of this article."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract Conflicts of Interest (COI) statements.

The COI Check module uses regular expressions to check sentences for words related to conflict of interest statements. It will return the sentences in which the conflict of interest statement was found.

The function incorporates code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This module was developed by Daniel Lakens

:::

### ℹ️ List All URLs {#list-all-urls .info}

...

::: {.callout-note title="How It Works" collapse="true"}

List all the URLs in the main text.

Checks for valid URLs using a regular expression.

This module was developed by Daniel Lakens

:::

### 🔍 Open Practices Check {#open-practices-check .yellow}

Shared data detected.

<details><summary>View detailed feedback</summary><div>

Data was openly shared for this article, based on the following text:

> Additional supporting information may be found at http://pss .sagepub.com/content/by/supplemental-data

We did not detect open sharing of code, which could be because there is no code related to this article, or the repository is not reconized by our code. If there is code, please consider sharing it in a repository.

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module searches for open data, code, materials, and registration statements.

It is much faster than the previous ODDPub version of this module, and has a lower false negative rate, but also a higher false positive rate.

This module was developed by Lisa DeBruine

:::

### ✅️ Ethics Approval Check {#ethics-approval-check .green}

All papers that appeared to involve live data collection contained an ethics approval statement.

<details><summary>View detailed feedback</summary><div>

Based on the following text, we would expect an ethics approval statement, and it was present:

> Participants were introduced to three people (in fact, experimental confederates), and the four-player group was given access to a resource of nominal value (points) that could be harvested and, after the experiment, converted into monetary payoffs.

> Participants provided informed consent after reading an information sheet indicating that the experiment would involve making decisions as part of a small group but not specifying all the details of, or the rationale for playing, the multiplayer resource-dilemma game.

> Thirty-two healthy adults were recruited from Oxford University and the local community; 24 were full-time students.

> In an initial session, all participants were assessed using a semistructured interview from the Structured Clinical Interview for DSM-IV-TR Axis I Disorders (First, Spitzer, Gibbon, & Williams, 2002).

> Participants completed measures of cognitive ability (Raven's Standard Progressive Matrices Sets A, B, C, D, & E;Raven, 1996) and impulsivity (Barratt Impulsiveness Scale; Patton, Stanford, & Barratt, 1995).

> During the harvesting phase (left panel), participants had 5 s to choose how much to harvest from the resource and enter that amount in the box marked "Select your take:."

> Participants were told that these points, accumulated over the whole game, could be exchanged for a real monetary reward at the end of the experiment (up to a maximum value of £15).

> On each harvesting opportunity, participants were allowed to harvest points by pressing the uparrow and down-arrow keys of a keyboard to scroll through integer values.

> This running-total mechanism dampened fluctuations in resource value over the course of the game, increased the number of harvesting opportunities that participants were likely to complete in a game, and facilitated the emergence of stable resource-management strategies (see the Supplemental Material for an example replenishment).

> After finishing the resource-dilemma game, participants completed a postgame questionnaire to measure their satisfaction with the game and the strategies that they employed.

> Converging evidence that tryptophan depletion suppressed the regulation of harvesting through diminished sensitivity to social norms is provided by the observation that, whereas the T-and T+ participants were equally happy with the outcomes of their resource-dilemma games and reported acting for their own benefit to a very similar extent, the T-participants reported significantly less concern about the best outcome for the wider group of players than the T+ participants.

Ethics approval statement:

> The experiment was approved by a National Health Service (England) research ethics committee.

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module searches for statements of ethics approval, IRB approval,
institutional review board approval, and related terms.

Patterns are designed to capture:

**Human research committee names**
- `Institutional Review Board` / IRB (US standard)
- `Independent Ethics Committee` / IEC (ICH-GCP international clinical trial term)
- `Ethical/Ethics Review Board` (generic)
- `Ethics (Advisory/Review) Committee/Board/Panel/Sub-committee`
- `Research Ethics Committee/Board/Panel` (UK/Canada/Australia)
- `Medical Ethics Committee`
- `Human Subjects/Research Committee` / `Human Research Ethics (Advisory) Panel`
- `Committee for/on the Protection of Human Subjects`
- `Committee on (Health) Research Ethics`
- `Office of Research Ethics`
- Abbreviations: IEC, REC, REB, ERB, METC, DEC. REC/REB/ERB/DEC are short
  enough to collide with unrelated jargon (e.g. `REC` as a recognition-heuristic
  model abbreviation, `DEC` as a decision-task label, `Reb` as an author surname),
  so these four require an ethics/approval/committee/board/panel/institutional/
  protocol word within ~30 characters in the same sentence. IRB and IEC are kept
  unconstrained as they are not observed to collide in practice.
- Dutch: `Medisch-ethische toetsingscommissie` (METC)
- French: `Comité d'éthique` / `Comité d'Ethique`

**Animal research committee names**
- `Institutional Animal Care and Use Committee` / IACUC (US standard)
- Any sentence containing `animal(s)` and `committee` (or `board`/`panel`) within ~5 words
  of each other — catches `Experimental Animal Care and Use Committee`,
  `Animal Ethics Committee`, `Animal Welfare Board`, `Animal Welfare Ethical Review Body`, etc.
- UK: `Animal Welfare Ethical Review Body` / AWERB
- Dutch: `Dierexperimentencommissie` / DEC (see DEC constraint above); `Instantie voor Dierenwelzijn` / IvD
- German: `Tierversuchskommission` / TvK (advisory committee under §15 Tierschutzgesetz)
- French: `Comité d'éthique en expérimentation animale` / CEEA; `Comité d'éthique animale`
- Spanish: `Comité de ética en experimentación animal` / CEEA

**Approval phrasing**
- `Ethics/Ethical (approval|clearance) [was] (granted|obtained|received|given|secured)`
- `Ethically approved`
- `Approved by the (ethics|irb|institutional|independent|local|review|research) ...`
- `This/The study/protocol/experiment/procedures/methods/research [was] (approved|reviewed) by`
- `Study was ethically approved`
- `(Followed|met|follow) the ethical (guidelines|standards|requirements)`
- `In accordance with ... ethical (guidelines|standards)`
- `Ethics protocol`
- `Approved under (protocol|reference|number)`

**Waiver / exemption**
- `Ethics/Ethical (waiver|exemption)`
- `IRB (waiver|exemption|exempt)`
- `Exempted from (ethics|irb|institutional review)`
- `Waived by the (ethics|irb|institutional|review) (committee|board)`
- `Deemed exempt`

**Declaration of Helsinki**
- `Declaration of Helsinki` / `Helsinki Declaration`

Patterns are NOT designed to capture:
- General ethical considerations or ethical dilemmas in study content
- Mentions of "ethics" in theoretical or philosophical contexts
- Author approval of a manuscript (e.g. "all authors approved the final version")
- Ethical behaviour as a measured variable (e.g. "ethical decision-making")
- URLs containing "ethics" in path components

Live data collection is detected by the internal helper `.detect_live_data()`,
which searches for sentences indicating that data were collected directly from
human or animal participants. Papers without any live-data signal are not
flagged as missing ethics approval. The helper uses conservative patterns to
avoid flagging secondary data analyses, computational experiments, or
economics papers that analyse existing survey data. See `.detect_live_data()`
for the full list of patterns and intentional exclusions.

:::

### ✅️ Funding Check (Overinclusive) {#funding-check-(overinclusive) .green}

A funding statement was detected.

<details><summary>View detailed feedback</summary><div>

The following funding statement was detected:

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("This work was supported by the Medical Research Council (Grant No. G0700410) and the Economic and Social Research Council (Grant No. ES/K002201/1)."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract funding statements.

The Funding Check module uses regular expressions to check sentences for words related to funding statements. It will return the sentences in which the conflict of interest statement was found.

The function is based on code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This version is over-inclusive, so will have more false positives, but is less likely to miss something.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

### ✅️ COI Check Overinclusive {#coi-check-overinclusive .green}

A conflict of interest statement was detected.

<details><summary>View detailed feedback</summary><div>

The following conflict of interest statement was detected.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("The authors declared that they had no conflicts of interest with respect to their authorship or the publication of this article."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract Conflicts of Interest (COI) statements.

The COI Check module uses regular expressions to check sentences for words related to conflict of interest statements. It will return the sentences in which the conflict of interest statement was found.

The function is based on code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This version is over-inclusive, so will have more false positives, but is less likely to miss something.

This module was developed by Daniel Lakens

:::

## Results Modules

### ⚠️ Exact P-Values {#exact-p-values .red}

We found 2 imprecise *p* values out of 13 detected *p* values.

<details><summary>View detailed feedback</summary><div>

Reporting *p* values imprecisely (e.g., *p* < .05) reduces transparency, reproducibility, and re-use (e.g., in *p* value meta-analyses). Best practice is to report exact p-values with three decimal places (e.g., *p* = .032) unless *p* values are smaller than 0.001, in which case you can use *p* < .001.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("P-Value" = c("p < .05", "p <.05"), Text = c("(Statistical significance was tested against a threshold of p < .05; bootstrapped models that provided 95% confidence intervals for the coefficients described below can be found in Table S2 in the Supplemental Material.)", 
"However, the T-participants did report thinking less about the best outcome for the group when completing the game (M = 2.75, SE = 0.34) than the T+ participants did (M = 4.00, SE = 0.41), β = -1.11 (SE = 0.50), p <.05."
)), row.names = c(NA, -2L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.1, 0.9), 2, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

The APA manual states: Report exact *p* values (e.g., *p* = .031) to two or three decimal places. However, report *p* values less than .001 as *p* < .001. However, 2 decimals is too imprecise for many use-cases (e.g., a *p* value meta-analysis), so report *p* values with three digits.

American Psychological Association (2020). <em>Publication manual of the American Psychological Association</em>, 7 edition. American Psychological Association.

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

List any p-values reported with insufficient precision (e.g., p < .05 or p = n.s.) or reported as exactly zero (e.g., p = .000).

This module uses regular expressions to identify p-values. It will flag any values reported as p > ? or p < numbers greater than .001. It will also flag p-values reported as exactly zero (e.g., p = .000, p = 0.00), which are mathematically impossible — p-values are never exactly zero and should instead be reported as p < .001.

We try to exclude figure and table notes like "* p < .05", but may not succeed at excluding all false positives.

This module only checks p-values reported in the running text of the manuscript. It cannot (yet) process p-values reported only in tables (as opposed to a table's footnote text, which the module does see and tries to exclude — see above).

This module was developed by Lisa DeBruine

:::

::: {.validation}
Validation: In a sample of 225 papers containing 405 instances of non-exact p-values, the module correctly detected 269 cases (true positives) and incorrectly identified 78 (false positives). It missed 136 instances of imprecisely reported p-values (false negatives) and correctly identified 4557 cases of precisely reported p-values (true negative). Additionally, 78% of positive detections were correct (positive predictive value).
:::

### ✅️ Non-Significant P Value Check {#non-significant-p-value-check .green}

We detected no nonsignificant p values.

::: {.callout-note title="How It Works" collapse="true"}

This module checks for imprecisely reported p values. If p > .05 is detected, it warns for misinterpretations.

The nonsignificant p-value check searches for regular expressions that match a predefined pattern. The module identifies all p-values in a manuscript and selects those that are not reported to be smaller than or equal to 0.05. It returns all sentences containing non-significant p-values.

In the future, the Metacheck team aims to incorporate a machine learning classifier to only return sentences likely to contain misinterpretations. If you want to help to improve the module, reach out to the Metacheck development team.

This module only checks p-values reported in the running text of the manuscript. It cannot (yet) process p-values reported only in tables.

This module was developed by Daniel Lakens

:::

::: {.validation}
Validation: In a sample of 194 papers with 1602 instances of non-significant p-values, this module correctly detected 1486 of them, and incorrectly identified 153. Additionally, 91% of detections were true instances (positive predictive value). That is, when this module flags non-significant p-values in a paper, it correctly identifies an issue 91% of the time.
:::

### ✅️ Marginal Significance {#marginal-significance .green}

You described 0 effects with terms related to 'marginally significant'.

No effects were described with terms related to 'marginally significant'.

::: {.callout-note title="How It Works" collapse="true"}

List all sentences that describe an effect as 'marginally significant'.

The marginal module searches for regular expressions that match a predefined pattern. The list of terms is a subset of those listed in a [blog post by Matthew Hankins](https://web.archive.org/web/20251001114321/https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/). The module returns all sentences that match terms describing ‘marginally significant’ results.

Some of the terms identified might not be problematic in some contexts, and there are ways to describe ‘marginal significance’ that are not detected by the module.

This module was developed by Daniel Lakens

:::

::: {.validation}
Validation: In a sample of 51 papers with 87 statements, this module correctly identified 38 statements (true positives) and incorrectly flagged 22 statements (false positives). It failed to detect 27 statements. Thus, among all statements flagged by the module, 63% were genuine cases (positive predictive value). However, the module missed 42% of all true statements (false negative rate).
:::

### ℹ️ List All P-Values {#list-all-p-values .info}

We found 13 p-values

<details><summary>View detailed feedback</summary><div>

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Text = c("p < .0001", "p < .0001", "p = .022", 
"p = .0002", "p =.0045", "p = .02", "p < .05", "p < .0001", "p < .0001", 
"p < .0001", "p = .02", "p <.05", "p < .005"), Sentence = c("As expected (Moore et al., 2000), plasma (total) tryptophan between baseline (immediately before receiving the amino-acid drink) and 5 hr later was reduced following the T-treatment but increased following the T+ treatment (see Table S1 in the Supplemental Material), β = -14.66 (SE = 1.26), p < .0001.", 
"Plasma tryptophan was reduced in the T-compared with the T+ participants just before participants began the resourcedilemma game, β = -14.38 (SE = 1.08), p < .0001.", 
"Eight of the T-participants (50% of the group) exhausted the resource completely, compared with only 2 of the T+ participants (12.5%), χ² (1, N = 32) = 5.24, p = .022.", 
"The T-participants also accumulated fewer points by the end of the game (Fig. 2a), β = -294.06 (SE = 79.39), p = .0002, and finished the game with smaller final resource values than the T+ participants (see Fig. 2b), β = -122.42 (SE = 43.06), p =.0045.", 
"The T-participants also accumulated fewer points by the end of the game (Fig. 2a), β = -294.06 (SE = 79.39), p = .0002, and finished the game with smaller final resource values than the T+ participants (see Fig. 2b), β = -122.42 (SE = 43.06), p =.0045.", 
"Overall, there was little evidence that the resource outcomes were consistently related to total or subscale scores of motor, attentional, and nonplanning impulsivity in either treatment group (-.25 < rs < .44); however, T-participants with higher nonplanning impulsivity scores did tend to accumulate larger totals of reward by the end of the game (r = .57, p = .02, uncorrected for the eight Pearson's correlation tests conducted).", 
"(Statistical significance was tested against a threshold of p < .05; bootstrapped models that provided 95% confidence intervals for the coefficients described below can be found in Table S2 in the Supplemental Material.)", 
"Model 1 showed that T+ participants tended to harvest more from higher value resources than from lower value resources (Table 2), β = 0.02 (SE = 0.001), p < .0001, and this behavior was not markedly altered in the T-compared with the T+ participants, β = 0.001 (SE = 0.002).", 
"Specifically, the T+ participants tended to reduce their harvests when they had taken larger harvests on the preceding harvesting opportunity, β = -0.69 (SE = 0.03), p < .0001, but then tended to increase their harvests when one or two other players were overharvesting, β = 0.88 (SE = 0.15), p < .0001.", 
"Specifically, the T+ participants tended to reduce their harvests when they had taken larger harvests on the preceding harvesting opportunity, β = -0.69 (SE = 0.03), p < .0001, but then tended to increase their harvests when one or two other players were overharvesting, β = 0.88 (SE = 0.15), p < .0001.", 
"By contrast, the tendency to reduce, or self-correct, harvests immediately following larger harvests was attenuated in the T-participants, β = 0.07 (SE = 0.03), p = .02.", 
"However, the T-participants did report thinking less about the best outcome for the group when completing the game (M = 2.75, SE = 0.34) than the T+ participants did (M = 4.00, SE = 0.41), β = -1.11 (SE = 0.50), p <.05.", 
"Asterisks indicate a significant difference between conditions ( * * * p < .005)."
)), row.names = c(NA, -13L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c("5em", NA), 2, FALSE)
```

This will catch most comparators like =<>~≈≠≤≥≪≫ and most versions of scientific notation like 5.0 x 10^-2 or 5.0e-2. If you find any formats that are not correctly handled by this function, please contact debruine@gmail.com.

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

List all p-values in the text, returning the matched text (e.g., 'p = 0.04') and document location in a table.

Note that this will not catch p-values reported like "the p-value is 0.03" because that results in a ton of false positives when papers discuss p-value thresholds. If you need to detect text like that, use `text_search()` function and a custom pattern like "\\bp(-| )?values?\\s+.{1,20}\\s+[0-9\\.]+"

This will catch most comparators like =<>~≈≠≤≥≪≫ and most versions of scientific notation like 5.0 x 10^-2 or 5.0e-2. If you find any formats that are not correctly handled by this function, please contact the author.

This module only checks p-values reported in the running text of the manuscript. It cannot (yet) process p-values reported only in tables.

This module was developed by Lisa DeBruine

:::

## Reference Modules

### ✅️ Reference Accuracy {#reference-accuracy .green}

We checked the 0 references that supplied a DOI against the record that DOI points to, and found 0 incoherent references to check for parsing errors or mistakes. 7 references had no DOI and could not be checked. Incoherent references are mostly PDF parsing errors (we are working on improving reference parsing). Adding a DOI to every reference that has one lets the other reference checks (retraction, PubPeer, and replication) run on them too.

<details><summary>View detailed feedback</summary><div>

### References without a DOI

These references have no DOI, so they could not be checked here, and they also cannot be checked by the other reference modules (retraction, PubPeer, and replication checks all rely on the DOI). We searched CrossRef for a matching DOI; where a confident match was found it is suggested below. We recommend adding a DOI to every reference that has one: it lets these checks run and makes each cited work easier to find and verify.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Reference = c("Booij, L., Van der Does, W., Benkelfat, C., Bremner, J. D., Cowen, P. J., Fava, M., . . . Van der Kloot, W. A. (2002). Predictors of mood response to acute tryptophan deple- tion: A reanalysis. Neuropsychopharmacology, 27, 852-861.", 
"Committee on the Human Dimensions of Global Change. (2002). The drama of the commons (E. Ostrom, T. Dietz, N. Dolsak, & P. C. Stern, Eds.). Washington, DC: National Academies Press.", 
"First, M. B., Spitzer, R. L., Gibbon, M., & Williams, J. B. W. (2002). Structured Clinical Interview for DSM-IV-TR Axis I Disorders-Patient edition (research version). New York, NY: Biometrics Research.", 
"Hardin, G. (1968). The tragedy of the commons. Science, 162, 1243-1248.", 
"Raven, J. (1996). Standard progressive matrices sets A, B, C, D & E. Oxford, England: Oxford Psychologists Press.", 
"Tanaka, S. C., Schweighofer, N., Asahi, S., Shishida, K., Okamoto, Y., Yamawaki, S., & Doya, K. (2007). Serotonin differentially regulates short-and long-term prediction of rewards in the ventral and dorsal striatum. PLoS ONE, 2(12), Article e1333. Retrieved from http://www.plosone.org/ article/info%3Adoi%2F10.1371%2Fjournal.pone.0001333", 
"Zhu, L., Gigerenzer, G., & Huangfu, G. (2013). Psychological traces of China's socio-economic reforms in the ulti- matum and dictator games. PLoS ONE, 8(8), Article e70769. Retrieved from http://www.plosone.org/article/ info%3Adoi%2F10.1371%2Fjournal.pone.0070769"
), "Suggested DOI" = c("", "", "", "", "", "", "")), row.names = c(NA, 
-7L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.7, 0.3), 5, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module checks whether each reference with a DOI is internally coherent: it compares the details the paper cites for a reference against the authoritative record that the reference's DOI points to, and flags any reference whose cited details do not match.

This module looks for *incoherent* references: a reference is incoherent when the title, authors, journal, or year that the paper cites disagree with the record that the reference's own DOI points to. Currently, it will most often be a parsing error where the reference list from the PDF is not extracted perfectly accurately, but the module can point out AI generated references, of mistakes in citations. You will need check the original source.

The module uses the `bib_match` table, which holds the metadata retrieved from CrossRef for each reference (added or refreshed with `add_bib_match()`, which makes live network calls).

**Only references that supply their own DOI are checked.** For these, we look up the record that exact DOI points to and compare it field by field against what the paper cites. A reference with no DOI is *not* checked: the only record we could find for it comes from a CrossRef title search, which often returns the wrong paper, so any "mismatch" would be CrossRef's error rather than the citation's. References without a DOI are instead listed separately, with a recommendation to add a DOI where one exists. For those, a suggested DOI is offered only when CrossRef found a high-confidence match (controlled by `suggest_score`).

For each checked reference we compare five fields against the DOI's record:

- **DOI** — flagged only when the reference printed a DOI that differs from the record (a blank cited DOI is never a mismatch).
- **Year** — flagged when the cited year is more than `year_tolerance` years from the record (online-first and print years routinely differ by one year, so this is allowed by default).
- **Journal** — flagged when the cited journal disagrees with the record. Journal names are matched tolerantly: standard ISO-4 abbreviations (e.g. "J. Pers. Soc. Psychol." for "Journal of Personality and Social Psychology"), "&"/"and", and "the" are treated as equivalent.
- **Title** — flagged when the cited title is too different from the record's title, judged by character-level similarity (`title_similarity`) after stripping case, punctuation, footnote markers and diacritics. This ignores cosmetic differences (colons, question marks, em-dash spacing, line-break word splits) while still catching a genuinely different title.
- **Authors** — flagged when the leading author surnames (the first `max_authors`) from the record are not all present in the cited author list. Only the leading authors are required because author lists are routinely truncated with "et al.". Diacritics are ignored, so "Gredebäck" and "Gredeback" match.

DOI, journal and year are reliable signals and flag a reference on their own. Title and author mismatches are more often caused by imperfect PDF parsing, so these are governed by `min_mismatches`: the default (1) flags a reference when either the title or the authors disagree. Set `min_mismatches = 2` to be more conservative and require both to disagree (fewer false positives, lower recall).

The report lists each incoherent reference with the specific cited value struck through and the record's value beside it, so the discrepancy is visible at a glance.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

::: {.validation}
Validation: In validation on psychology references with a DOI, the module flagged genuine, coherent references at a low rate: around 8% of checked references at the default setting (min_mismatches = 1), and about 3% with the more conservative setting (min_mismatches = 2). On deliberately corrupted references it caught journal and year fabrications reliably (about 96-100%) at either setting, and essentially all single-field fabrications (including single title or author changes) at min_mismatches = 1. Importantly, in a hand-review of references flagged across 10 papers from 5 fields, the large majority of flags were imperfect extraction of the reference from the PDF (for example a journal name mis-parsed, or two references merged) rather than genuine citation errors. Real citation mistakes are rare, so even though the false positive rate is low, a flag should be read as "check this reference against the original source", not as a confirmed error.
:::

### ℹ️ Summarise References {#summarise-references .info}

Summary information provided for 38 references

<details><summary>View detailed feedback</summary><div>

See the specific reports above for details.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(text = c("Barclay, P. (2004). Trustworthiness and competitive altruism can also solve the \"tragedy of the commons.\" Evolution and Human Behavior, 25, 209-220.", 
"Biel, A., & Thøgersen, J. (2007). Activation of social norms in social dilemmas: A review of the evidence and reflections on the implications for environmental behaviour. Journal of Economic Psychology, 28, 93-112.", 
"Booij, L., Van der Does, W., Benkelfat, C., Bremner, J. D., Cowen, P. J., Fava, M., . . . Van der Kloot, W. A. (2002). Predictors of mood response to acute tryptophan deple- tion: A reanalysis. Neuropsychopharmacology, 27, 852-861.", 
"Boyce, C. J., Brown, G. D. A., & Moore, S. C. (2010). Money and happiness: Rank of income, not income, affects life satisfac- tion. Psychological Science, 21, 471-475.", 
"Burke, B. E. (2001). Hardin revisited: A critical look at percep- tion and the logic of the commons. Human Ecology, 29, 449-476.", 
"Campbell, W. K., Bush, C. P., Brunell, A. B., & Shelton, J. (2005). Understanding the social costs of narcissism: The case of the tragedy of the commons. Personality and Social Psychology Bulletin, 31, 1358-1368.", 
"Committee on the Human Dimensions of Global Change. (2002). The drama of the commons (E. Ostrom, T. Dietz, N. Dolsak, & P. C. Stern, Eds.). Washington, DC: National Academies Press.", 
"Crockett, M. J., Apergis-Schoute, A., Herrmann, B., Lieberman, M., Müller, U., Robbins, T. W., & Clark, L. (2013). Serotonin modulates striatal responses to fairness and retaliation in humans. Journal of Neuroscience, 33, 3505-3513.", 
"Crockett, M. J., Clark, L., Tabibnia, G., Lieberman, M. D., & Robbins, T. W. (2008). Serotonin modulates behavioral reactions to unfairness. Science, 320, 1739.", 
"Dougherty, D. M., Bjork, J. M., Marsh, D. M., & Moeller, F. G. (1999). Influence of trait hostility on tryptophan depletion- induced laboratory aggression. Psychiatry Research, 88, 227-232.", 
"Feeny, D., Berkes, F., McCay, B. J., & Acheson, J. M. (1990). The tragedy of the commons: Twenty-two years later. Human Ecology, 18, 1-19.", 
"Fehr, E., & Gächter, S. (2002). Altruistic punishment in humans. Nature, 415, 137-140.", 
"First, M. B., Spitzer, R. L., Gibbon, M., & Williams, J. B. W. (2002). Structured Clinical Interview for DSM-IV-TR Axis I Disorders-Patient edition (research version). New York, NY: Biometrics Research.", 
"Fischbacher, U., & Gächter, S. (2010). Social preferences, beliefs, and the dynamics of free riding in public good experiments. American Economic Review, 100, 541-556.", 
"Fischbacher, U., Gächter, S., & Fehr, E. (2001). Are people conditionally cooperative? Evidence from a public goods experiment. Economics Letters, 71, 397-404.", 
"Gardiner, S. M. (2001). The real tragedy of the commons. Philosophy & Public Affairs, 30, 387-416.", 
"Hardin, G. (1968). The tragedy of the commons. Science, 162, 1243-1248.", 
"Jager, W., Janssen, M. A., & Vlek, C. A. J. (2002). How uncer- tainty stimulates over-harvesting in a resource dilemma: Three possible explanations. Journal of Environmental Psychology, 22, 247-263.", 
"Knutson, B., Wolkowitz, O. M., Cole, S. W., Chan, T., Moore, E. A., Johnson, R. C., . . . Reus, V. I. (1998). Selective alteration of personality and social behavior by serotonergic interven- tion. American Journal of Psychiatry, 155, 373-379.", 
"Koenigs, M., & Tranel, D. (2007). Irrational economic decision- making after ventromedial prefrontal damage: Evidence from the ultimatum game. Journal of Neuroscience, 27, 951-956.", 
"Kollock, P. (1998). Social dilemmas: The anatomy of coopera- tion. Annual Review of Sociology, 24, 183-214.", 
"Melrose, K. L., Brown, G. D. A., & Wood, A. M. (2012). Am I abnormal? Relative rank and social norm effects in judg- ments of anxiety and depression symptom severity. Journal of Behavioral Decision Making, 26, 174-184.", 
"Moore, P., Landolt, H. P., Seifritz, E., Clark, C., Bhatti, T., Kelsoe, J., . . . Gillin, J. C. (2000). Clinical and physi- ological consequences of rapid tryptophan depletion. Neuropsychopharmacology, 23, 601-622.", 
"Nolan, J. M., Schultz, P. W., Cialdini, R. B., Goldstein, N. J., & Griskevicius, V. (2008). Normative social influence is underdetected. Personality and Social Psychology Bulletin, 34, 913-923.", 
"Ostrom, E. (2000). Reformulating the commons. Swiss Political Science Review, 6(1), 29-52.", 
"Ostrom, E. (2009). A general framework for analyzing sustain- ability of social-ecological systems. Science, 325, 419-422.", 
"Patton, J. H., Stanford, M. S., & Barratt, E. S. (1995). Factor struc- ture of the Barratt Impulsiveness Scale. Journal of Clinical Psychology, 51, 768-774.", 
"Raleigh, M. J., McGuire, M. T., Brammer, G. L., Pollack, D. B., & Yuwiler, A. (1991). Serotonergic mechanisms promote dominance acquisition in adult male vervet monkeys. Brain Research, 559, 181-190.", 
"Rankin, D. J., Bargum, K., & Kokko, H. (2007). The tragedy of the commons in evolutionary biology. Trends in Ecology & Evolution, 22, 643-651.", 
"Raven, J. (1996). Standard progressive matrices sets A, B, C, D & E. Oxford, England: Oxford Psychologists Press.", 
"Ruhe, H. G., Mason, N. S., & Schene, A. H. (2007). Mood is indi- rectly related to serotonin, norepinephrine and dopamine levels in humans: A meta-analysis of monoamine depletion studies. Molecular Psychiatry, 12, 331-359.", 
"Schweighofer, N., Bertin, M., Shishida, K., Okamoto, Y., Tanaka, S. C., Yamawaki, S., & Doya, K. (2008). Low-serotonin lev- els increase delayed reward discounting in humans. Journal of Neuroscience, 28, 4528-4532.", 
"Tanaka, S. C., Schweighofer, N., Asahi, S., Shishida, K., Okamoto, Y., Yamawaki, S., & Doya, K. (2007). Serotonin differentially regulates short-and long-term prediction of rewards in the ventral and dorsal striatum. PLoS ONE, 2(12), Article e1333. Retrieved from http://www.plosone.org/ article/info%3Adoi%2F10.1371%2Fjournal.pone.0001333", 
"Thøgersen, J. (2008). Social norms and cooperation in real- life social dilemmas. Journal of Economic Psychology, 29, 458-472.", 
"Watson, D., Clark, L. A., & Tellegen, A. (1988). Development and validation of brief measures of positive and negative affect: The PANAS scales. Journal of Personality and Social Psychology, 54, 1063-1070.", 
"Wood, A. M., Boyce, C. J., Moore, S. C., & Brown, G. D. A. (2012). An evolutionary based social rank explanation of why low income predicts mental distress: A 17 year cohort study of 30,000 people. Journal of Affective Disorders, 136, 882-888.", 
"Wood, R. M., Rilling, J. K., Sanfey, A. G., Bhagwagar, Z., & Rogers, R. D. (2006). Effects of tryptophan depletion on the performance of an iterated prisoner's dilemma game in healthy adults. Neuropsychopharmacology, 31, 1075-1084.", 
"Zhu, L., Gigerenzer, G., & Huangfu, G. (2013). Psychological traces of China's socio-economic reforms in the ulti- matum and dictator games. PLoS ONE, 8(8), Article e70769. Retrieved from http://www.plosone.org/article/ info%3Adoi%2F10.1371%2Fjournal.pone.0070769"
), accuracy_mismatch = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, "year, container", NA, NA, 
NA, "year, container, title, author", NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA)), row.names = c(NA, -38L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.75, NA), 10, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Summarise information about each reference in a paper.

This module summarises previously-run reference section modules: ref_accuracy, ref_pubpeer, ref_replication, and ref_retraction.

This module was developed by Lisa DeBruine

:::

### ⚠️ Reference Consistency {#reference-consistency .red}

There are cross-references that are not in the bibliography and/or bibliography entries not cross-referenced in the text

<details><summary>View detailed feedback</summary><div>

This module relies on Grobid correctly parsing the references. There are likley to be some false positives.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(bib_id = c(6L, NA, NA, NA), type = c("extra", 
"missing", "missing", "missing"), contents = c(NA, "Change, 2002;", 
"(Raven's Standard Progressive Matrices Sets A, B, C, D, & E;", 
"Change, 2002;"), reference = c("Committee on the Human Dimensions of Global Change. (2002). The drama of the commons (E. Ostrom, T. Dietz, N. Dolsak, & P. C. Stern, Eds.). Washington, DC: National Academies Press.", 
"Humans, like other socialized species, must work together to manage the exploitation of valuable but finite resources (Committee on the Human Dimensions of Global Change, 2002;Ostrom, 2009).", 
"Participants completed measures of cognitive ability (Raven's Standard Progressive Matrices Sets A, B, C, D, & E;Raven, 1996) and impulsivity (Barratt Impulsiveness Scale; Patton, Stanford, & Barratt, 1995).", 
"Our laboratory multiplayer resource-dilemma game was also only a very approximate model of real-world resource dilemmas, as it involved no immediate survival or economic imperatives (Committee on the Human Dimensions of Global Change, 2002;Gardiner, 2001;Ostrom, 2009) or sanctions known to promote socially cooperative behavior in common-pool problems (Fehr & Gächter, 2002)."
)), row.names = c(NA, -4L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Check if all references are cited and all citations are referenced

This module is currently under development and should not be relied on until we have increased the accuracy of the reference labeling while importing papers. It has a high false-positive rate because grobid (the PDF-importing tool) tends to miss some references and falsely identify some text as citations.

This module was developed by Lisa DeBruine

:::

### ✅️ Miscitation {#miscitation .green}

We detected no miscited papers

::: {.callout-note title="How It Works" collapse="true"}

Check for frequently miscited papers. This module is just a proof of concept -- the miscite database is not yet populated with real examples.

If you want to use your own database, create a data frame with the columns "doi", "reftext", and "warning", which will be used to match the DOI in papers (use short DOIs like xxx/1234, not https://doi.org/xxx/1234) and produce the report text.

This module was developed by Lisa DeBruine

:::




