---
title: MetaCheck Report
subtitle: "Beyond Gist: Strategic and Incremental Information Accumulation for Scene Categorization"
metacheck:
  version: "0.3.1 (pytacheck 0.3.1.dev1)"
  report-created: "2026-09-25"
format:
  html:
    theme: 
      light: flatly
      dark: darkly
    respect-user-color-scheme: true
    toc: true
    toc-title: >
      <ul class="emoji-key">
        <li class="red">⚠️ possible problems detected;</li> 
        <li class="yellow">🔍 something to check;</li> 
        <li class="green">✅️ no problems detected;</li>  
        <li class="info">ℹ️ informational only;</li>  
        <li class="na">⬜ not applicable;</li>  
        <li class="fail">☠️ check failed</li>
      <ul>
      <hr/>
      **Table of Contents**
    toc-location: right
    toc-expand: 3
    page-layout: full
    title-block-banner: "#15342A"    #"#327118"
    title-block-banner-color: "white"
    link-external-newwindow: true
    embed-resources: true
    format-links: false
    smooth-scroll: true
execute: 
  echo: false
  error: true
---

<style>
  #TOC * { border-left: none; }
  #TOC > ul { border-left: 1px solid #15342A; }
  #TOC > ul > li > ul > li { text-indent: -1.2em; margin-left: 1.2em; }
  main h2, main h3 { margin-left: -20px; }
  main h2 { font-size: 150%; font-face: italics; }
  main h3 { font-size: 125%; }
  main h4 { font-size: 110%; }
  .emoji-key li { margin-bottom: 0.5em; }
  section::before { content: '' !important; }
  th { background-color: #555; color: white; }
  table.dataTable, .dataTables_scrollBody { margin: 0.5em 0; }
  #info { position: absolute; top: 2.5em; right: 2.5em; color: white; }
  #info a { color: white !important; }
  .quarto-dark tr.even { background-color: #333; }
  .quarto-dark tr.odd { background-color: #222; }
  .quarto-dark div.datatables { color: white; }
  .quarto-dark table.dataTable { border: 1px solid #555; }
  table strong { color: red; }
  .quarto-dark table strong { color: yellow; }
  summary { color: #333; }
  .quarto-dark summary { color: #CCC; }
  .validation { display: block; 
                border: 2px solid #15342A; 
                border-radius: 1em; 
                padding: 0.5em 1em 0; 
                margin-bottom: 0.5em;
                background-color: #15342A33;}
</style>

::: {#info}
[MetaCheck](http://www.scienceverse.org/metacheck) version {{< meta metacheck.version >}}  
Report Created: {{< meta metacheck.report-created >}}  
DOI: [10.1177/0956797614522816](https://doi.org/10.1177/0956797614522816) <!-- doi, if exists -->
:::

[Metacheck](https://www.scienceverse.org/metacheck/) is a tool that screens scientific manuscripts and aims to identify potential issues for improvement. Our goal is to guide researchers towards best practices, especially with respect to practices that researchers easily forget, or might not have learned about yet. Metacheck is developed to help researchers correctly and completely report statistical results, will point to possibly relevant information about citations, and provides feedback about data and code sharing.

Metacheck combines existing and new checks in a module-based tool. It is open source, and anyone can contribute modules. It mainly relies on text search or retrieving information from external sources through API’s or web-scraping, but the power modules can optionally use large language models. The use of LLM's is always optional and opt-in. The development of Metacheck is guided by our [values statement](https://www.scienceverse.org/metacheck/#our-values).

::: {.validation}
In light with our values, our modules are validated on sets of open-access papers. In each validated module, there will be a sentence explaining the prevalence of false positives (incorrect detection/classification) and false negatives (incorrect omission). For example, if a hypothetical module detects the inappropriate practice of "woozling", the sentence might read:

> In a sample of 250 papers from the *Journal of X*, there were 350 instances of woozling. This module correctly detected 340 of them, and incorrectly identified 7. Therefore 3% of true instances are missed, and 2% of detections are false positives.

There is an inherent tradeoff between false positives and false negatives. Many of our modules are designed like "smoke detectors", where they are more likely to detect a practice that needs attention, but also more likely to incorrectly flag something. Therefore, you need to check the output of each module, keeping the validated error rates in mind.
:::

Metacheck is under continuous development. It can be surprisingly difficult to automatically retrieve information from papers, and there is a large amount of edge-cases where our tool might not yet work accurately. By using our tool, and providing us with feedback about what we can't get right yet, you will help to improve the tool for all other users. Issues can be submitted [on Github](https://github.com/scienceverse/metacheck/issues), and suggestions for improvement or feedback can be sent to [metacheck@scienceverse.org](mailto:metacheck@scienceverse.org).


## Summary

- ✅️ [Funding Check](#funding-check){.green}: A funding statement was detected.  
- ✅️ [COI Check](#coi-check){.green}: A conflict of interest statement was detected.  
- ⬜ [List All URLs](#list-all-urls){.na}:   
- ⚠️ [Open Practices Check](#open-practices-check){.red}: Neither shared data nor code detected.  
- ⚠️ [Ethics Approval Check](#ethics-approval-check){.red}: 1 of 1 paper appeared to involve live data collection and lacked an ethics approval statement.  
- ✅️ [Funding Check (Overinclusive)](#funding-check-(overinclusive)){.green}: A funding statement was detected.  
- ✅️ [COI Check Overinclusive](#coi-check-overinclusive){.green}: A conflict of interest statement was detected.  
- ⬜ [Preregistration Check](#preregistration-check){.na}: No preregistration links were found.  
- ⬜ [Power Analysis Check](#power-analysis-check){.na}: No power analyses were detected.  
- ⬜ [Repository Check](#repository-check){.na}: We found no links to repositories on the Open Science Framework, Github, ResearchBox, DSpace, Zenodo, Dataverse, Figshare, Dryad, ReShare, 4TU.ResearchData, Mendeley Data, or DataONE.  
- ⬜ [Code Check](#code-check){.na}: We found 0 R, 0 Python, 0 SAS, 0 SPSS, 0 Stata, 0 Mplus, 0 MATLAB, and 0 JASP code files.  
- ✅️ [StatCheck](#statcheck){.green}: We detected no errors in t-tests or F-tests.  
- ✅️ [Exact P-Values](#exact-p-values){.green}: We found no imprecise *p* values or *p*-values of exactly zero out of 39 detected.  
- 🔍 [Non-Significant P Value Check](#non-significant-p-value-check){.yellow}: We found 17 non-significant p values that should be checked for appropriate interpretation.  
- ⚠️ [Effect Sizes in t-tests and F-tests](#effect-sizes-in-t-tests-and-f-tests){.red}: We found 2 t-tests and/or F-tests where effect sizes are not reported. Check these tests in the table below, and consider adding effect sizes  
- ✅️ [Marginal Significance](#marginal-significance){.green}: You described 0 effects with terms related to 'marginally significant'.  
- ℹ️ [List All P-Values](#list-all-p-values){.info}: We found 39 p-values  
- ⬜ [Data Check](#data-check){.na}: We found no files to analyse.  
- ⬜ [Codebook Check](#codebook-check){.na}: We found no extracted data columns to check against a codebook.  
- ⬜ [Psych-DS Check](#psych-ds-check){.na}: We found no repository files to check for Psych-DS compliance.  
- ⬜ [Reproducibility Check](#reproducibility-check){.na}: 
    -  We found no R code files to assess for reproducibility.  
- ✅️ [Reference Accuracy](#reference-accuracy){.green}: We checked the 0 references that supplied a DOI against the record that DOI points to, and found 0 incoherent references to check for parsing errors or mistakes. 3 references had no DOI and could not be checked. Incoherent references are mostly PDF parsing errors (we are working on improving reference parsing). Adding a DOI to every reference that has one lets the other reference checks (retraction, PubPeer, and replication) run on them too.  
- ⬜ [Replication Check](#replication-check){.na}: No citations to articles in the FLoRA database were found.  
- ⬜ [RetractionWatch](#retractionwatch){.na}: No citations to articles in the RetractionWatch database were found.  
- ℹ️ [Summarise References](#summarise-references){.info}: Summary information provided for 26 references  
- ⚠️ [Reference Consistency](#reference-consistency){.red}: There are cross-references that are not in the bibliography and/or bibliography entries not cross-referenced in the text  
- ✅️ [Miscitation](#miscitation){.green}: We detected no miscited papers  
- ☠️ [ref_pubpeer](#ref_pubpeer){.fail}: This module failed to run  



## General Modules

### ✅️ Funding Check {#funding-check .green}

A funding statement was detected.

<details><summary>View detailed feedback</summary><div>

The following funding statement was detected:

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("Funding G. L. Malcolm was supported by Economic and Social Research Council Grant PTA-026-27-2500."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract funding statements.

The Funding Check module uses regular expressions to check sentences for words related to funding statements. It will return the sentences in which the conflict of interest statement was found.

The function incorporates code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This module was developed by Daniel Lakens

:::

### ✅️ COI Check {#coi-check .green}

A conflict of interest statement was detected.

<details><summary>View detailed feedback</summary><div>

The following conflict of interest statement was detected.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("The authors declared that they had no conflicts of interest with respect to their authorship or the publication of this article."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract Conflicts of Interest (COI) statements.

The COI Check module uses regular expressions to check sentences for words related to conflict of interest statements. It will return the sentences in which the conflict of interest statement was found.

The function incorporates code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This module was developed by Daniel Lakens

:::

### ⚠️ Open Practices Check {#open-practices-check .red}

Neither shared data nor code detected.

::: {.callout-note title="How It Works" collapse="true"}

This module searches for open data, code, materials, and registration statements.

It is much faster than the previous ODDPub version of this module, and has a lower false negative rate, but also a higher false positive rate.

This module was developed by Lisa DeBruine

:::

### ⚠️ Ethics Approval Check {#ethics-approval-check .red}

1 of 1 paper appeared to involve live data collection and lacked an ethics approval statement.

<details><summary>View detailed feedback</summary><div>

Based on the following text, we would expect an ethics approval statement, but it was not present:

> All reported normal or corrected-to-normal vision and gave informed consent before participating.

> However, it is not clear what participants were doing during this time: If participants in the subordinate condition used the extra time to accrue HSF information to facilitate their judgment, they should have made more eye movements than participants in the basic condition.

> Participants were asked to categorize individual scenes, but unlike in the gazecontingent experiment, each scene contained objects identified as diagnostic at either the basic level (example shown on left) or subordinate level (example shown in middle).

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module searches for statements of ethics approval, IRB approval,
institutional review board approval, and related terms.

Patterns are designed to capture:

**Human research committee names**
- `Institutional Review Board` / IRB (US standard)
- `Independent Ethics Committee` / IEC (ICH-GCP international clinical trial term)
- `Ethical/Ethics Review Board` (generic)
- `Ethics (Advisory/Review) Committee/Board/Panel/Sub-committee`
- `Research Ethics Committee/Board/Panel` (UK/Canada/Australia)
- `Medical Ethics Committee`
- `Human Subjects/Research Committee` / `Human Research Ethics (Advisory) Panel`
- `Committee for/on the Protection of Human Subjects`
- `Committee on (Health) Research Ethics`
- `Office of Research Ethics`
- Abbreviations: IEC, REC, REB, ERB, METC, DEC. REC/REB/ERB/DEC are short
  enough to collide with unrelated jargon (e.g. `REC` as a recognition-heuristic
  model abbreviation, `DEC` as a decision-task label, `Reb` as an author surname),
  so these four require an ethics/approval/committee/board/panel/institutional/
  protocol word within ~30 characters in the same sentence. IRB and IEC are kept
  unconstrained as they are not observed to collide in practice.
- Dutch: `Medisch-ethische toetsingscommissie` (METC)
- French: `Comité d'éthique` / `Comité d'Ethique`

**Animal research committee names**
- `Institutional Animal Care and Use Committee` / IACUC (US standard)
- Any sentence containing `animal(s)` and `committee` (or `board`/`panel`) within ~5 words
  of each other — catches `Experimental Animal Care and Use Committee`,
  `Animal Ethics Committee`, `Animal Welfare Board`, `Animal Welfare Ethical Review Body`, etc.
- UK: `Animal Welfare Ethical Review Body` / AWERB
- Dutch: `Dierexperimentencommissie` / DEC (see DEC constraint above); `Instantie voor Dierenwelzijn` / IvD
- German: `Tierversuchskommission` / TvK (advisory committee under §15 Tierschutzgesetz)
- French: `Comité d'éthique en expérimentation animale` / CEEA; `Comité d'éthique animale`
- Spanish: `Comité de ética en experimentación animal` / CEEA

**Approval phrasing**
- `Ethics/Ethical (approval|clearance) [was] (granted|obtained|received|given|secured)`
- `Ethically approved`
- `Approved by the (ethics|irb|institutional|independent|local|review|research) ...`
- `This/The study/protocol/experiment/procedures/methods/research [was] (approved|reviewed) by`
- `Study was ethically approved`
- `(Followed|met|follow) the ethical (guidelines|standards|requirements)`
- `In accordance with ... ethical (guidelines|standards)`
- `Ethics protocol`
- `Approved under (protocol|reference|number)`

**Waiver / exemption**
- `Ethics/Ethical (waiver|exemption)`
- `IRB (waiver|exemption|exempt)`
- `Exempted from (ethics|irb|institutional review)`
- `Waived by the (ethics|irb|institutional|review) (committee|board)`
- `Deemed exempt`

**Declaration of Helsinki**
- `Declaration of Helsinki` / `Helsinki Declaration`

Patterns are NOT designed to capture:
- General ethical considerations or ethical dilemmas in study content
- Mentions of "ethics" in theoretical or philosophical contexts
- Author approval of a manuscript (e.g. "all authors approved the final version")
- Ethical behaviour as a measured variable (e.g. "ethical decision-making")
- URLs containing "ethics" in path components

Live data collection is detected by the internal helper `.detect_live_data()`,
which searches for sentences indicating that data were collected directly from
human or animal participants. Papers without any live-data signal are not
flagged as missing ethics approval. The helper uses conservative patterns to
avoid flagging secondary data analyses, computational experiments, or
economics papers that analyse existing survey data. See `.detect_live_data()`
for the full list of patterns and intentional exclusions.

:::

### ✅️ Funding Check (Overinclusive) {#funding-check-(overinclusive) .green}

A funding statement was detected.

<details><summary>View detailed feedback</summary><div>

The following funding statement was detected:

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("Funding G. L. Malcolm was supported by Economic and Social Research Council Grant PTA-026-27-2500."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract funding statements.

The Funding Check module uses regular expressions to check sentences for words related to funding statements. It will return the sentences in which the conflict of interest statement was found.

The function is based on code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This version is over-inclusive, so will have more false positives, but is less likely to miss something.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

### ✅️ COI Check Overinclusive {#coi-check-overinclusive .green}

A conflict of interest statement was detected.

<details><summary>View detailed feedback</summary><div>

The following conflict of interest statement was detected.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list("The authors declared that they had no conflicts of interest with respect to their authorship or the publication of this article."), names = "", class = "data.frame", row.names = c(NA, 
-1L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Identify and extract Conflicts of Interest (COI) statements.

The COI Check module uses regular expressions to check sentences for words related to conflict of interest statements. It will return the sentences in which the conflict of interest statement was found.

The function is based on code from [rtransparent](https://github.com/serghiou/rtransparent), which is no longer maintained. For their validation, see [the paper](https://doi.org/10.1371/journal.pbio.3001107).

This version is over-inclusive, so will have more false positives, but is less likely to miss something.

This module was developed by Daniel Lakens

:::

## Results Modules

### ✅️ StatCheck {#statcheck .green}

We detected no errors in t-tests or F-tests.

::: {.callout-note title="How It Works" collapse="true"}

Check consistency of p-values and test statistics

The Statcheck module runs Statcheck. Statcheck searches for regular expressions that match a predefined pattern, and identifies APA reported statistical tests. More information on the package can be found at <https://github.com/cran/statcheck>. The module only returns Statcheck results for t-tests and F-tests, as these are the only tests which have been validated, see <https://osf.io/preprints/psyarxiv/tcxaj_v1/>.

Statcheck was developed by Michèle Nuijten and Sascha Epskamp.

Statcheck considers p = 0.000 an error, as you should report p < 0.001. Furthermore, p < 0.03 is an error if the p-value was 0.031, and one should simply report exact p-values (p = 0.031). Statcheck might miss one-sided tests, and falsely assume the p-value is incorrect. For more information, see [StatCheck](https://statcheck.io/).

This module only checks statistical results reported in the running text of the manuscript. It cannot (yet) process statistics reported only in tables.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

::: {.validation}
Validation: In a sample of 685 tests with 34 instances of inconsistent reporting, Statcheck correctly detected 34 of them, and incorrectly identified 26. Therefore 0% of true instances were missed, and 43% of detections were false positives. See <https://osf.io/preprints/psyarxiv/tcxaj_v1/> for more details of the validation.
:::

### ✅️ Exact P-Values {#exact-p-values .green}

We found no imprecise *p* values or *p*-values of exactly zero out of 39 detected.

::: {.callout-note title="How It Works" collapse="true"}

List any p-values reported with insufficient precision (e.g., p < .05 or p = n.s.) or reported as exactly zero (e.g., p = .000).

This module uses regular expressions to identify p-values. It will flag any values reported as p > ? or p < numbers greater than .001. It will also flag p-values reported as exactly zero (e.g., p = .000, p = 0.00), which are mathematically impossible — p-values are never exactly zero and should instead be reported as p < .001.

We try to exclude figure and table notes like "* p < .05", but may not succeed at excluding all false positives.

This module only checks p-values reported in the running text of the manuscript. It cannot (yet) process p-values reported only in tables (as opposed to a table's footnote text, which the module does see and tries to exclude — see above).

This module was developed by Lisa DeBruine

:::

::: {.validation}
Validation: In a sample of 225 papers containing 405 instances of non-exact p-values, the module correctly detected 269 cases (true positives) and incorrectly identified 78 (false positives). It missed 136 instances of imprecisely reported p-values (false negatives) and correctly identified 4557 cases of precisely reported p-values (true negative). Additionally, 78% of positive detections were correct (positive predictive value).
:::

### 🔍 Non-Significant P Value Check {#non-significant-p-value-check .yellow}

We found 17 non-significant p values that should be checked for appropriate interpretation.

<details><summary>View detailed feedback</summary><div>

Meta-scientific research has shown nonsignificant p values are commonly misinterpreted. It is incorrect to infer that there is 'no effect', 'no difference', or that groups are 'the same' after p > 0.05.

It is possible that there is a true non-zero effect, but that the study did not detect it. Make sure your inference acknowledges that it is possible that there is a non-zero effect. It is correct to include the effect is 'not significantly' different, although this just restates that p > 0.05.

Metacheck does not yet analyze automatically whether sentences which include non-significant p-values are correct, but we recommend manually checking the sentences below for possible misinterpreted non-significant p values.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Text = c("p = .153", "p = .315", "p = .09", "p = .122", 
"p = .237", "p = .156", "p = .121", "p = .072", "p = .151", "p = .070", 
"p = .058", "p = .055", "p = .068", "p = .203", "p = .288", "p = .299", 
"p = .094"), Sentence = c("There was also a main effect of stimuli type, F(3, 78) = 12.910, p < .001, ηp² = .332 (Ms = 2,832, 2,709, 3,419, and 2,157 ms for classrooms, pools, restaurants, and roads, respectively), but no interaction between the two factors, F(3, 78) = 1.805, p = .153, ηp² = .065 (Table 1).", 
"There was also a main effect of stimuli type, F(3, 78) = 9.558, p < .001, ηp² = .269 (Ms = 7.76, 7.23, 9.36, and 5.89 for classrooms, pools, restaurants, and roads, respectively), but no interaction, F(3, 78) = 1.201, p = .315, ηp² = .044 (Table 1).", 
"There was a main effect of judgment on fixation duration, F(1, 26) = 8.246, p = .008, ηp² = .241 (basic: M = 381 ms; subordinate: M = 300 ms), a trend for stimuli type, F(3, 78) = 2.242, p = .09, ηp² = .079 (Ms = 329, 354, 341, and 335 ms for classrooms, pools, restaurants, and roads, respectively), as well as a significant interaction, F(3, 78) = 3.207, p = .028, ηp² = .110.", 
"This interaction occurred because participants in the basic condition had numerically longer fixations when categorizing pool scenes (M = 383 ms) compared with participants in the subordinate condition (M = 325 ms), t(26) = 1.598, p = .122; fixation durations for all other scenes were significant, ts > 2.370, ps < .025 (Table 1).", 
"There was no interaction, F(3, 78) = 1.444, p = .237, ηp² = .053.", 
"For the sake of completeness, there was no main effect of judgment, F(1, 22) = 2.163, p = .156, ηp² = .090, though there was an effect of stimuli type, F(3, 66) = 4.342, p = .007, ηp² = .165 (Ms = 3.88°, 3.47°, 3.87°, and 3.52° for classrooms, pools, restaurants, and roads, respectively) as well as of ordinal fixation, F(2.286, 50.288) = 42.240, p < .001, ηp² = .658 (Ms = 2.55°, 3.28°, 3.86°, 4.26°, and 4.48° from the center for Fixations 1 through 5, respectively).", 
"There was no interaction between stimuli type and ordinal count (F < 1), no interaction between judgment and stimuli type, F(3, 66) = 2.012, p = .121, ηp² = .084, and no three-way interaction (F < 1).", 
"There was also a trend for an interaction, F(1, 34) = 3.456, p = .072, ηp² = .092 (Fig. 6), which was due to a significant change in subordinate categorization accuracy when basic or subordinate diagnostic objects were visible (Ms = .65 and .76, respectively), t(17) = 4.134, p = .001, but no significant difference during basic categorization (basic diagnostic objects: M = .77 and subordinate diagnostic objects: M = .81), t(17) = 1.506, p = .151.", 
"There was also a trend for an interaction, F(1, 34) = 3.456, p = .072, ηp² = .092 (Fig. 6), which was due to a significant change in subordinate categorization accuracy when basic or subordinate diagnostic objects were visible (Ms = .65 and .76, respectively), t(17) = 4.134, p = .001, but no significant difference during basic categorization (basic diagnostic objects: M = .77 and subordinate diagnostic objects: M = .81), t(17) = 1.506, p = .151.", 
"During these normal viewing conditions, there was a strong trend of judgment on RT, F(1, 26) = 3.568, p = .070, ηp² = .121, with basic categorization needing less time (1,062 ms) than subordinate categorization (1,272 ms).", 
"There was a main effect of stimuli type, F(2.084, 54.188) = 7.080, p = .002, ηp² = .214 (Ms = 1,269, 1,128, 1,273, and 998 ms for classrooms, pools, restaurants, and roads, respectively) as well as a trend for an interaction, F(3, 78) = 2.596, p = .058, ηp² = .091, which was due to restaurants taking significantly longer to categorize at the subordinate level (M = 1,471 ms) than at the basic level (M = 1,075 ms), t(26) = 3.00, p = .006.", 
"There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
"There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
"For initial saccade latency, there was no main effect of judgment, F(1, 26) = 1.708, p = .203, ηp² = .062, or stimuli type, nor was there an interaction between the two for initial saccade latency (Fs < 1).", 
"There was no interaction, F(3, 78) = 1.276, p = .288, ηp² = .047.", 
"No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094.", 
"No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094."
)), row.names = c(NA, -17L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.1, 0.9), 10, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating the rate of misinterpretations of non-significant results is high, see:

Aczel B, Palfi B, Szollosi A, Kovacs M, Szaszi B, Szecsi P, Zrubka M, Gronau Q, van den Bergh D, Wagenmakers E (2018). &ldquo;Quantifying Support for the Null Hypothesis in Psychology: An Empirical Investigation.&rdquo; <em>Advances in Methods and Practices in Psychological Science</em>, <b>1</b>(3), 357&ndash;366. <a href="https://doi.org/10.1177/2515245918773742">doi:10.1177/2515245918773742</a>.

Murphy S, Merz R, Reimann L, Fernández A (2025). &ldquo;Nonsignificance misinterpreted as an effect’s absence in psychology: Prevalence and temporal analyses.&rdquo; <em>Royal Society Open Science</em>, <b>12</b>(3), 242167. <a href="https://doi.org/10.1098/rsos.242167">doi:10.1098/rsos.242167</a>.

For educational material on preventing the misinterpretation of p values, see [Improving Your Statistical Inferences](https://lakens.github.io/statistical_inferences/01-pvalue.html#sec-misconception1).

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module checks for imprecisely reported p values. If p > .05 is detected, it warns for misinterpretations.

The nonsignificant p-value check searches for regular expressions that match a predefined pattern. The module identifies all p-values in a manuscript and selects those that are not reported to be smaller than or equal to 0.05. It returns all sentences containing non-significant p-values.

In the future, the Metacheck team aims to incorporate a machine learning classifier to only return sentences likely to contain misinterpretations. If you want to help to improve the module, reach out to the Metacheck development team.

This module only checks p-values reported in the running text of the manuscript. It cannot (yet) process p-values reported only in tables.

This module was developed by Daniel Lakens

:::

::: {.validation}
Validation: In a sample of 194 papers with 1602 instances of non-significant p-values, this module correctly detected 1486 of them, and incorrectly identified 153. Additionally, 91% of detections were true instances (positive predictive value). That is, when this module flags non-significant p-values in a paper, it correctly identifies an issue 91% of the time.
:::

### ⚠️ Effect Sizes in t-tests and F-tests {#effect-sizes-in-t-tests-and-f-tests .red}

We found 2 t-tests and/or F-tests where effect sizes are not reported. Check these tests in the table below, and consider adding effect sizes

<details><summary>View detailed feedback</summary><div>

We recommend checking the sentences below, and add any missing effect sizes.

For t-tests with a reported d, coherence checks yielded 6 indeterminate cases.

For F-tests with a reported eta-squared effect size, coherence checks yielded 27 matches under assumptions, 1 no match.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(c("This interaction occurred because participants in the basic condition had numerically longer fixations when categorizing pool scenes (M = 383 ms) compared with participants in the subordinate condition (M = 325 ms), t(26) = 1.598, p = .122; fixation durations for all other scenes were significant, ts > 2.370, ps < .025 (Table 1).", 
"In contrast, there were similar, but not significant, numerical patterns for classrooms (basic: M = 3.81°; subordinate: M = 4.31°) and pools (basic: M = 3.04°; subordinate: M = 3.63°), ts < 1.560, ps > .131, whereas for roads, there were longer saccades in the basic condition (M = 3.61°) than in the subordinate condition (M = 3.27°), t <1."
)), names = "", class = "data.frame", row.names = c(NA, -2L))

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

::: {.callout-tip title="Learn More" collapse="true"}

For metascientific articles demonstrating that effect sizes are often not reported:

* Peng, C.-Y. J., Chen, L.-T., Chiang, H.-M., & Chiang, Y.-C. (2013). The Impact of APA and AERA Guidelines on Effect Size Reporting. Educational Psychology Review, 25(2), 157–209. doi:[10.1007/s10648-013-9218-2](https://doi.org/10.1007/s10648-013-9218-2).

For educational material on reporting effect sizes:

* [Guide to Effect Sizes and Confidence Intervals](https://matthewbjane.quarto.pub/guide-to-effect-sizes-and-confidence-intervals/)

:::

::: {.callout-tip title="All detected and assessed stats" collapse="true"}

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Sentence = c("We found a main effect of judgment on response time (RT); processing was faster in the basic condition (M = 2,305 ms) than in the subordinate condition (M = 3,253 ms), F(1, 26) = 9.277, p = .005, ηp² = .263.", 
"There was also a main effect of stimuli type, F(3, 78) = 12.910, p < .001, ηp² = .332 (Ms = 2,832, 2,709, 3,419, and 2,157 ms for classrooms, pools, restaurants, and roads, respectively), but no interaction between the two factors, F(3, 78) = 1.805, p = .153, ηp² = .065 (Table 1).", 
"There was also a main effect of stimuli type, F(3, 78) = 12.910, p < .001, ηp² = .332 (Ms = 2,832, 2,709, 3,419, and 2,157 ms for classrooms, pools, restaurants, and roads, respectively), but no interaction between the two factors, F(3, 78) = 1.805, p = .153, ηp² = .065 (Table 1).", 
"We found a main effect of judgment on fixation count, with more fixations made during subordinate categorizations (M = 9.72) than during basic categorizations (M = 5.40), F(1, 26) = 17.906, p < .001, ηp² = .408.", 
"There was also a main effect of stimuli type, F(3, 78) = 9.558, p < .001, ηp² = .269 (Ms = 7.76, 7.23, 9.36, and 5.89 for classrooms, pools, restaurants, and roads, respectively), but no interaction, F(3, 78) = 1.201, p = .315, ηp² = .044 (Table 1).", 
"There was also a main effect of stimuli type, F(3, 78) = 9.558, p < .001, ηp² = .269 (Ms = 7.76, 7.23, 9.36, and 5.89 for classrooms, pools, restaurants, and roads, respectively), but no interaction, F(3, 78) = 1.201, p = .315, ηp² = .044 (Table 1).", 
"There was a main effect of judgment, F(1, 26) = 5.720, p = .024, ηp² = .180, with basic categorizations having longer saccade latencies (M = 421 ms) than subordinate categorizations (M = 352 ms), but no effect of stimuli type or interaction with judgment (Fs < 1; Table 1).", 
"There was a main effect of judgment on fixation duration, F(1, 26) = 8.246, p = .008, ηp² = .241 (basic: M = 381 ms; subordinate: M = 300 ms), a trend for stimuli type, F(3, 78) = 2.242, p = .09, ηp² = .079 (Ms = 329, 354, 341, and 335 ms for classrooms, pools, restaurants, and roads, respectively), as well as a significant interaction, F(3, 78) = 3.207, p = .028, ηp² = .110.", 
"There was a main effect of judgment on fixation duration, F(1, 26) = 8.246, p = .008, ηp² = .241 (basic: M = 381 ms; subordinate: M = 300 ms), a trend for stimuli type, F(3, 78) = 2.242, p = .09, ηp² = .079 (Ms = 329, 354, 341, and 335 ms for classrooms, pools, restaurants, and roads, respectively), as well as a significant interaction, F(3, 78) = 3.207, p = .028, ηp² = .110.", 
"There was a main effect of judgment on fixation duration, F(1, 26) = 8.246, p = .008, ηp² = .241 (basic: M = 381 ms; subordinate: M = 300 ms), a trend for stimuli type, F(3, 78) = 2.242, p = .09, ηp² = .079 (Ms = 329, 354, 341, and 335 ms for classrooms, pools, restaurants, and roads, respectively), as well as a significant interaction, F(3, 78) = 3.207, p = .028, ηp² = .110.", 
"This interaction occurred because participants in the basic condition had numerically longer fixations when categorizing pool scenes (M = 383 ms) compared with participants in the subordinate condition (M = 325 ms), t(26) = 1.598, p = .122; fixation durations for all other scenes were significant, ts > 2.370, ps < .025 (Table 1).", 
"There was no effect of judgment on saccade amplitudes (F < 1); however, as one would expect given the different layouts between the different category groups, there was a main effect of stimuli type, F(3, 78) = 5.882, p = .001, ηp² = .184 (Ms = 2.75°, 2.31°, 2.72°, and 2.51° for classrooms, pools, restaurants, and roads, respectively; Table 1).", 
"There was no interaction, F(3, 78) = 1.444, p = .237, ηp² = .053.", 
"A three-way mixed-design 2 (judgment: basic, subordinate) × 4 (stimuli type: classroom, pool, restaurant, road) × 5 (ordinal fixation: 1, 2, 3, 4, 5) ANOVA on fixation distance from screen center revealed a critical interaction between judgment and ordinal fixation, F(4, 88) = 3.661, p = .008, ηp² = .143; this interaction indicates that participants carried out different sampling strategies over the first five fixations depending on the judgment they were assigned to make (Fig. 4).", 
"For the sake of completeness, there was no main effect of judgment, F(1, 22) = 2.163, p = .156, ηp² = .090, though there was an effect of stimuli type, F(3, 66) = 4.342, p = .007, ηp² = .165 (Ms = 3.88°, 3.47°, 3.87°, and 3.52° for classrooms, pools, restaurants, and roads, respectively) as well as of ordinal fixation, F(2.286, 50.288) = 42.240, p < .001, ηp² = .658 (Ms = 2.55°, 3.28°, 3.86°, 4.26°, and 4.48° from the center for Fixations 1 through 5, respectively).", 
"For the sake of completeness, there was no main effect of judgment, F(1, 22) = 2.163, p = .156, ηp² = .090, though there was an effect of stimuli type, F(3, 66) = 4.342, p = .007, ηp² = .165 (Ms = 3.88°, 3.47°, 3.87°, and 3.52° for classrooms, pools, restaurants, and roads, respectively) as well as of ordinal fixation, F(2.286, 50.288) = 42.240, p < .001, ηp² = .658 (Ms = 2.55°, 3.28°, 3.86°, 4.26°, and 4.48° from the center for Fixations 1 through 5, respectively).", 
"There was no interaction between stimuli type and ordinal count (F < 1), no interaction between judgment and stimuli type, F(3, 66) = 2.012, p = .121, ηp² = .084, and no three-way interaction (F < 1).", 
"Analyses revealed a main effect of judgment on accuracy, F(1, 34) = 9.339, p = .004, ηp² = .215 (basic: M = .79; subordinate: M = .71) and a main effect of diagnostic information, F(1, 34) = 15.871, p < .001, ηp² = .318 (basic: M = .71; subordinate: M = .79).", 
"Analyses revealed a main effect of judgment on accuracy, F(1, 34) = 9.339, p = .004, ηp² = .215 (basic: M = .79; subordinate: M = .71) and a main effect of diagnostic information, F(1, 34) = 15.871, p < .001, ηp² = .318 (basic: M = .71; subordinate: M = .79).", 
"There was also a trend for an interaction, F(1, 34) = 3.456, p = .072, ηp² = .092 (Fig. 6), which was due to a significant change in subordinate categorization accuracy when basic or subordinate diagnostic objects were visible (Ms = .65 and .76, respectively), t(17) = 4.134, p = .001, but no significant difference during basic categorization (basic diagnostic objects: M = .77 and subordinate diagnostic objects: M = .81), t(17) = 1.506, p = .151.", 
"There was also a trend for an interaction, F(1, 34) = 3.456, p = .072, ηp² = .092 (Fig. 6), which was due to a significant change in subordinate categorization accuracy when basic or subordinate diagnostic objects were visible (Ms = .65 and .76, respectively), t(17) = 4.134, p = .001, but no significant difference during basic categorization (basic diagnostic objects: M = .77 and subordinate diagnostic objects: M = .81), t(17) = 1.506, p = .151.", 
"There was also a trend for an interaction, F(1, 34) = 3.456, p = .072, ηp² = .092 (Fig. 6), which was due to a significant change in subordinate categorization accuracy when basic or subordinate diagnostic objects were visible (Ms = .65 and .76, respectively), t(17) = 4.134, p = .001, but no significant difference during basic categorization (basic diagnostic objects: M = .77 and subordinate diagnostic objects: M = .81), t(17) = 1.506, p = .151.", 
"During these normal viewing conditions, there was a strong trend of judgment on RT, F(1, 26) = 3.568, p = .070, ηp² = .121, with basic categorization needing less time (1,062 ms) than subordinate categorization (1,272 ms).", 
"There was a main effect of stimuli type, F(2.084, 54.188) = 7.080, p = .002, ηp² = .214 (Ms = 1,269, 1,128, 1,273, and 998 ms for classrooms, pools, restaurants, and roads, respectively) as well as a trend for an interaction, F(3, 78) = 2.596, p = .058, ηp² = .091, which was due to restaurants taking significantly longer to categorize at the subordinate level (M = 1,471 ms) than at the basic level (M = 1,075 ms), t(26) = 3.00, p = .006.", 
"There was a main effect of stimuli type, F(2.084, 54.188) = 7.080, p = .002, ηp² = .214 (Ms = 1,269, 1,128, 1,273, and 998 ms for classrooms, pools, restaurants, and roads, respectively) as well as a trend for an interaction, F(3, 78) = 2.596, p = .058, ηp² = .091, which was due to restaurants taking significantly longer to categorize at the subordinate level (M = 1,471 ms) than at the basic level (M = 1,075 ms), t(26) = 3.00, p = .006.", 
"Fixation counts showed a similar pattern of results, with basic categorization requiring fewer fixations (M = 2.95) than subordinate categorization (M = 4.01), F(1, 26) = 5.391, p = .028, ηp² = .172.", 
"There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
"There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
"There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
"For initial saccade latency, there was no main effect of judgment, F(1, 26) = 1.708, p = .203, ηp² = .062, or stimuli type, nor was there an interaction between the two for initial saccade latency (Fs < 1).", 
"There was no interaction, F(3, 78) = 1.276, p = .288, ηp² = .047.", 
"No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094.", 
"No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094.", 
"No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094.", 
"No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094.", 
"In contrast, there were similar, but not significant, numerical patterns for classrooms (basic: M = 3.81°; subordinate: M = 4.31°) and pools (basic: M = 3.04°; subordinate: M = 3.63°), ts < 1.560, ps > .131, whereas for roads, there were longer saccades in the basic condition (M = 3.61°) than in the subordinate condition (M = 3.27°), t <1."
), "Effect Size" = c("ηp² = .263", "ηp² = .332", "ηp² = .065", 
"ηp² = .408", "ηp² = .269", "ηp² = .044", "ηp² = .180", 
"ηp² = .241", "ηp² = .079", "ηp² = .110", NA, "ηp² = .184", 
"ηp² = .053", "ηp² = .143", "ηp² = .090; ηp² = .165; ηp² = .658", 
"ηp² = .090; ηp² = .165; ηp² = .658", "ηp² = .084", "ηp² = .215", 
"ηp² = .318", "ηp² = .092", "ηp² = .092", "ηp² = .092", 
"ηp² = .121", "ηp² = .214", "ηp² = .091", "ηp² = .172", 
"ηp² = .241; ηp² = .092", "ηp² = .241; ηp² = .092", "ηp² = .241; ηp² = .092", 
"ηp² = .062", "ηp² = .047", "ηp² = .041; ηp² = .445; ηp² = .158", 
"ηp² = .041; ηp² = .445; ηp² = .158", "ηp² = .041; ηp² = .445; ηp² = .158", 
"ηp² = .041; ηp² = .445; ηp² = .158", NA), "Reported Test" = c("F(1, 26) = 9.277", 
"F(3, 78) = 12.910", "F(3, 78) = 1.805", "F(1, 26) = 17.906", 
"F(3, 78) = 9.558", "F(3, 78) = 1.201", "F(1, 26) = 5.720", "F(1, 26) = 8.246", 
"F(3, 78) = 2.242", "F(3, 78) = 3.207", "t(26) = 1.598", "F(3, 78) = 5.882", 
"F(3, 78) = 1.444", "F(4, 88) = 3.661", "F(1, 22) = 2.163", "F(3, 66) = 4.342", 
"F(3, 66) = 2.012", "F(1, 34) = 9.339", "F(1, 34) = 15.871", 
"F(1, 34) = 3.456", "t(17) = 4.134", "t(17) = 1.506", "F(1, 26) = 3.568", 
"F(3, 78) = 2.596", "t(26) = 3.00", "F(1, 26) = 5.391", "F(3, 78) = 2.637", 
"t(26) = 1.901", "t(26) = 3.363", "F(1, 26) = 1.708", "F(3, 78) = 1.276", 
"F(1, 26) = 1.122", "F(3, 78) = 20.836", "F(3, 78) = 4.869", 
"t(26) = 1.735", "t < 1"), "Test Type" = c("F-test", "F-test", 
"F-test", "F-test", "F-test", "F-test", "F-test", "F-test", "F-test", 
"F-test", "t-test", "F-test", "F-test", "F-test", "F-test", "F-test", 
"F-test", "F-test", "F-test", "F-test", "t-test", "t-test", "F-test", 
"F-test", "t-test", "F-test", "F-test", "t-test", "t-test", "F-test", 
"F-test", "F-test", "F-test", "F-test", "t-test", "t-test"), 
    "d Coherence" = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    "indeterminate", NA, NA, NA, NA, NA, NA, NA, NA, NA, "indeterminate", 
    "indeterminate", NA, NA, "indeterminate", NA, NA, "indeterminate", 
    "indeterminate", NA, NA, NA, NA, NA, "indeterminate", "indeterminate"
    ), "d Assumption" = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, 
    NA, "none", NA, NA, NA, NA, NA, NA, NA, NA, NA, "none", "none", 
    NA, NA, "none", NA, NA, "none", "none", NA, NA, NA, NA, NA, 
    "none", "none"), "d Coherence Note" = c(NA, NA, NA, NA, NA, 
    NA, NA, NA, NA, NA, "No parseable d effect size found.", 
    NA, NA, NA, NA, NA, NA, NA, NA, NA, "No parseable d effect size found.", 
    "No parseable d effect size found.", NA, NA, "No parseable d effect size found.", 
    NA, NA, "No parseable d effect size found.", "No parseable d effect size found.", 
    NA, NA, NA, NA, NA, "No parseable d effect size found.", 
    "No parseable t(df)=value found."), "eta Coherence" = c("match_under_assumptions", 
    "match_under_assumptions", "match_under_assumptions", "match_under_assumptions", 
    "match_under_assumptions", "match_under_assumptions", "match_under_assumptions", 
    "match_under_assumptions", "match_under_assumptions", "match_under_assumptions", 
    NA, "match_under_assumptions", "match_under_assumptions", 
    "match_under_assumptions", "match_under_assumptions", "match_under_assumptions", 
    "match_under_assumptions", "match_under_assumptions", "match_under_assumptions", 
    "match_under_assumptions", NA, NA, "match_under_assumptions", 
    "no_match", NA, "match_under_assumptions", "match_under_assumptions", 
    NA, NA, "match_under_assumptions", "match_under_assumptions", 
    "match_under_assumptions", "match_under_assumptions", "match_under_assumptions", 
    NA, NA), "eta Assumption" = c("partial_eta_squared", "partial_eta_squared", 
    "partial_eta_squared", "partial_eta_squared", "partial_eta_squared", 
    "partial_eta_squared", "partial_eta_squared", "partial_eta_squared", 
    "partial_eta_squared", "partial_eta_squared", NA, "partial_eta_squared", 
    "partial_eta_squared", "partial_eta_squared", "partial_eta_squared", 
    "partial_eta_squared", "partial_eta_squared", "partial_eta_squared", 
    "partial_eta_squared", "partial_eta_squared", NA, NA, "partial_eta_squared", 
    "partial_eta_squared", NA, "partial_eta_squared", "partial_eta_squared", 
    NA, NA, "partial_eta_squared", "partial_eta_squared", "partial_eta_squared", 
    "partial_eta_squared", "partial_eta_squared", NA, NA), "eta Coherence Note" = c("Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    NA, "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    NA, NA, "Match under partial eta-squared formula from F and dfs.", 
    "No match under partial eta-squared formula from F and dfs. Tolerance = 0.01. A no-match can occur when fewer than 2 decimal places are reported.", 
    NA, "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    NA, NA, "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    "Match under partial eta-squared formula from F and dfs.", 
    NA, NA)), row.names = c(NA, -36L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, "auto", 5, FALSE)
```

:::

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

The Effect Size module checks if effect sizes are correctly reported in t-tests and F-tests.

The Effect Size check searches for regular expressions that match typical ways in which effect sizes are reported. It subsequently checks different ways in which Cohen's d, g, ηp2, and ωp2 can be computed against the reported value. If effects are missing, or might be incorrect, you the module provides a warning. The module was validated on APA reported statistical tests, and might miss effect sizes that were reported in other reporting styles. It was validated by the Metacheck team on papers published in Psychological Science.

This module only checks statistical results reported in the running text of the manuscript. It cannot (yet) process statistics reported only in tables.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

::: {.validation}
Validation: In a sample of 161 papers with 1469 tests, this module correctly detected 1106 reported effect sizes (true positives) and correctly identified 295 cases where no effect size was present (true negatives). However, it missed 23 that were reported (false negatives), and incorrectly identified 45 effect sizes when none were reported (false positives). Among all instances detected by the module, 96% were true cases (positive predictive value). In a validation against 221 reported Cohen's d effect sizes, it correctly indicated coherence in 218 cases (99%). In a validation against 485 partial eta-squared effect sizes, it correctly indicated coherence in 480 (99%)
:::

### ✅️ Marginal Significance {#marginal-significance .green}

You described 0 effects with terms related to 'marginally significant'.

No effects were described with terms related to 'marginally significant'.

::: {.callout-note title="How It Works" collapse="true"}

List all sentences that describe an effect as 'marginally significant'.

The marginal module searches for regular expressions that match a predefined pattern. The list of terms is a subset of those listed in a [blog post by Matthew Hankins](https://web.archive.org/web/20251001114321/https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/). The module returns all sentences that match terms describing ‘marginally significant’ results.

Some of the terms identified might not be problematic in some contexts, and there are ways to describe ‘marginal significance’ that are not detected by the module.

This module was developed by Daniel Lakens

:::

::: {.validation}
Validation: In a sample of 51 papers with 87 statements, this module correctly identified 38 statements (true positives) and incorrectly flagged 22 statements (false positives). It failed to detect 27 statements. Thus, among all statements flagged by the module, 63% were genuine cases (positive predictive value). However, the module missed 42% of all true statements (false negative rate).
:::

### ℹ️ List All P-Values {#list-all-p-values .info}

We found 39 p-values

<details><summary>View detailed feedback</summary><div>

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Text = c("p = .005", "p < .001", "p = .153", "p < .001", 
"p < .001", "p = .315", "p = .024", "p = .008", "p = .09", "p = .028", 
"p = .122", "p = .001", "p = .237", "p = .008", "p = .156", "p = .007", 
"p < .001", "p = .121", "p = .004", "p < .001", "p = .072", "p = .001", 
"p = .151", "p = .070", "p = .002", "p = .058", "p = .006", "p = .028", 
"p = .001", "p = .055", "p = .068", "p = .002", "p = .203", "p = .011", 
"p = .288", "p = .299", "p < .001", "p = .004", "p = .094"), 
    Sentence = c("We found a main effect of judgment on response time (RT); processing was faster in the basic condition (M = 2,305 ms) than in the subordinate condition (M = 3,253 ms), F(1, 26) = 9.277, p = .005, ηp² = .263.", 
    "There was also a main effect of stimuli type, F(3, 78) = 12.910, p < .001, ηp² = .332 (Ms = 2,832, 2,709, 3,419, and 2,157 ms for classrooms, pools, restaurants, and roads, respectively), but no interaction between the two factors, F(3, 78) = 1.805, p = .153, ηp² = .065 (Table 1).", 
    "There was also a main effect of stimuli type, F(3, 78) = 12.910, p < .001, ηp² = .332 (Ms = 2,832, 2,709, 3,419, and 2,157 ms for classrooms, pools, restaurants, and roads, respectively), but no interaction between the two factors, F(3, 78) = 1.805, p = .153, ηp² = .065 (Table 1).", 
    "We found a main effect of judgment on fixation count, with more fixations made during subordinate categorizations (M = 9.72) than during basic categorizations (M = 5.40), F(1, 26) = 17.906, p < .001, ηp² = .408.", 
    "There was also a main effect of stimuli type, F(3, 78) = 9.558, p < .001, ηp² = .269 (Ms = 7.76, 7.23, 9.36, and 5.89 for classrooms, pools, restaurants, and roads, respectively), but no interaction, F(3, 78) = 1.201, p = .315, ηp² = .044 (Table 1).", 
    "There was also a main effect of stimuli type, F(3, 78) = 9.558, p < .001, ηp² = .269 (Ms = 7.76, 7.23, 9.36, and 5.89 for classrooms, pools, restaurants, and roads, respectively), but no interaction, F(3, 78) = 1.201, p = .315, ηp² = .044 (Table 1).", 
    "There was a main effect of judgment, F(1, 26) = 5.720, p = .024, ηp² = .180, with basic categorizations having longer saccade latencies (M = 421 ms) than subordinate categorizations (M = 352 ms), but no effect of stimuli type or interaction with judgment (Fs < 1; Table 1).", 
    "There was a main effect of judgment on fixation duration, F(1, 26) = 8.246, p = .008, ηp² = .241 (basic: M = 381 ms; subordinate: M = 300 ms), a trend for stimuli type, F(3, 78) = 2.242, p = .09, ηp² = .079 (Ms = 329, 354, 341, and 335 ms for classrooms, pools, restaurants, and roads, respectively), as well as a significant interaction, F(3, 78) = 3.207, p = .028, ηp² = .110.", 
    "There was a main effect of judgment on fixation duration, F(1, 26) = 8.246, p = .008, ηp² = .241 (basic: M = 381 ms; subordinate: M = 300 ms), a trend for stimuli type, F(3, 78) = 2.242, p = .09, ηp² = .079 (Ms = 329, 354, 341, and 335 ms for classrooms, pools, restaurants, and roads, respectively), as well as a significant interaction, F(3, 78) = 3.207, p = .028, ηp² = .110.", 
    "There was a main effect of judgment on fixation duration, F(1, 26) = 8.246, p = .008, ηp² = .241 (basic: M = 381 ms; subordinate: M = 300 ms), a trend for stimuli type, F(3, 78) = 2.242, p = .09, ηp² = .079 (Ms = 329, 354, 341, and 335 ms for classrooms, pools, restaurants, and roads, respectively), as well as a significant interaction, F(3, 78) = 3.207, p = .028, ηp² = .110.", 
    "This interaction occurred because participants in the basic condition had numerically longer fixations when categorizing pool scenes (M = 383 ms) compared with participants in the subordinate condition (M = 325 ms), t(26) = 1.598, p = .122; fixation durations for all other scenes were significant, ts > 2.370, ps < .025 (Table 1).", 
    "There was no effect of judgment on saccade amplitudes (F < 1); however, as one would expect given the different layouts between the different category groups, there was a main effect of stimuli type, F(3, 78) = 5.882, p = .001, ηp² = .184 (Ms = 2.75°, 2.31°, 2.72°, and 2.51° for classrooms, pools, restaurants, and roads, respectively; Table 1).", 
    "There was no interaction, F(3, 78) = 1.444, p = .237, ηp² = .053.", 
    "A three-way mixed-design 2 (judgment: basic, subordinate) × 4 (stimuli type: classroom, pool, restaurant, road) × 5 (ordinal fixation: 1, 2, 3, 4, 5) ANOVA on fixation distance from screen center revealed a critical interaction between judgment and ordinal fixation, F(4, 88) = 3.661, p = .008, ηp² = .143; this interaction indicates that participants carried out different sampling strategies over the first five fixations depending on the judgment they were assigned to make (Fig. 4).", 
    "For the sake of completeness, there was no main effect of judgment, F(1, 22) = 2.163, p = .156, ηp² = .090, though there was an effect of stimuli type, F(3, 66) = 4.342, p = .007, ηp² = .165 (Ms = 3.88°, 3.47°, 3.87°, and 3.52° for classrooms, pools, restaurants, and roads, respectively) as well as of ordinal fixation, F(2.286, 50.288) = 42.240, p < .001, ηp² = .658 (Ms = 2.55°, 3.28°, 3.86°, 4.26°, and 4.48° from the center for Fixations 1 through 5, respectively).", 
    "For the sake of completeness, there was no main effect of judgment, F(1, 22) = 2.163, p = .156, ηp² = .090, though there was an effect of stimuli type, F(3, 66) = 4.342, p = .007, ηp² = .165 (Ms = 3.88°, 3.47°, 3.87°, and 3.52° for classrooms, pools, restaurants, and roads, respectively) as well as of ordinal fixation, F(2.286, 50.288) = 42.240, p < .001, ηp² = .658 (Ms = 2.55°, 3.28°, 3.86°, 4.26°, and 4.48° from the center for Fixations 1 through 5, respectively).", 
    "For the sake of completeness, there was no main effect of judgment, F(1, 22) = 2.163, p = .156, ηp² = .090, though there was an effect of stimuli type, F(3, 66) = 4.342, p = .007, ηp² = .165 (Ms = 3.88°, 3.47°, 3.87°, and 3.52° for classrooms, pools, restaurants, and roads, respectively) as well as of ordinal fixation, F(2.286, 50.288) = 42.240, p < .001, ηp² = .658 (Ms = 2.55°, 3.28°, 3.86°, 4.26°, and 4.48° from the center for Fixations 1 through 5, respectively).", 
    "There was no interaction between stimuli type and ordinal count (F < 1), no interaction between judgment and stimuli type, F(3, 66) = 2.012, p = .121, ηp² = .084, and no three-way interaction (F < 1).", 
    "Analyses revealed a main effect of judgment on accuracy, F(1, 34) = 9.339, p = .004, ηp² = .215 (basic: M = .79; subordinate: M = .71) and a main effect of diagnostic information, F(1, 34) = 15.871, p < .001, ηp² = .318 (basic: M = .71; subordinate: M = .79).", 
    "Analyses revealed a main effect of judgment on accuracy, F(1, 34) = 9.339, p = .004, ηp² = .215 (basic: M = .79; subordinate: M = .71) and a main effect of diagnostic information, F(1, 34) = 15.871, p < .001, ηp² = .318 (basic: M = .71; subordinate: M = .79).", 
    "There was also a trend for an interaction, F(1, 34) = 3.456, p = .072, ηp² = .092 (Fig. 6), which was due to a significant change in subordinate categorization accuracy when basic or subordinate diagnostic objects were visible (Ms = .65 and .76, respectively), t(17) = 4.134, p = .001, but no significant difference during basic categorization (basic diagnostic objects: M = .77 and subordinate diagnostic objects: M = .81), t(17) = 1.506, p = .151.", 
    "There was also a trend for an interaction, F(1, 34) = 3.456, p = .072, ηp² = .092 (Fig. 6), which was due to a significant change in subordinate categorization accuracy when basic or subordinate diagnostic objects were visible (Ms = .65 and .76, respectively), t(17) = 4.134, p = .001, but no significant difference during basic categorization (basic diagnostic objects: M = .77 and subordinate diagnostic objects: M = .81), t(17) = 1.506, p = .151.", 
    "There was also a trend for an interaction, F(1, 34) = 3.456, p = .072, ηp² = .092 (Fig. 6), which was due to a significant change in subordinate categorization accuracy when basic or subordinate diagnostic objects were visible (Ms = .65 and .76, respectively), t(17) = 4.134, p = .001, but no significant difference during basic categorization (basic diagnostic objects: M = .77 and subordinate diagnostic objects: M = .81), t(17) = 1.506, p = .151.", 
    "During these normal viewing conditions, there was a strong trend of judgment on RT, F(1, 26) = 3.568, p = .070, ηp² = .121, with basic categorization needing less time (1,062 ms) than subordinate categorization (1,272 ms).", 
    "There was a main effect of stimuli type, F(2.084, 54.188) = 7.080, p = .002, ηp² = .214 (Ms = 1,269, 1,128, 1,273, and 998 ms for classrooms, pools, restaurants, and roads, respectively) as well as a trend for an interaction, F(3, 78) = 2.596, p = .058, ηp² = .091, which was due to restaurants taking significantly longer to categorize at the subordinate level (M = 1,471 ms) than at the basic level (M = 1,075 ms), t(26) = 3.00, p = .006.", 
    "There was a main effect of stimuli type, F(2.084, 54.188) = 7.080, p = .002, ηp² = .214 (Ms = 1,269, 1,128, 1,273, and 998 ms for classrooms, pools, restaurants, and roads, respectively) as well as a trend for an interaction, F(3, 78) = 2.596, p = .058, ηp² = .091, which was due to restaurants taking significantly longer to categorize at the subordinate level (M = 1,471 ms) than at the basic level (M = 1,075 ms), t(26) = 3.00, p = .006.", 
    "There was a main effect of stimuli type, F(2.084, 54.188) = 7.080, p = .002, ηp² = .214 (Ms = 1,269, 1,128, 1,273, and 998 ms for classrooms, pools, restaurants, and roads, respectively) as well as a trend for an interaction, F(3, 78) = 2.596, p = .058, ηp² = .091, which was due to restaurants taking significantly longer to categorize at the subordinate level (M = 1,471 ms) than at the basic level (M = 1,075 ms), t(26) = 3.00, p = .006.", 
    "Fixation counts showed a similar pattern of results, with basic categorization requiring fewer fixations (M = 2.95) than subordinate categorization (M = 4.01), F(1, 26) = 5.391, p = .028, ηp² = .172.", 
    "There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
    "There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
    "There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
    "There was also a main effect of stimuli type, F(1.909, 49.641) = 8.239, p = .001, ηp² = .241 (Ms = 3.96, 3.21, 3.85, and 2.89 for classrooms, pools, restaurants, and roads, respectively), and a trend for an interaction, F(3, 78) = 2.637, p = .055, ηp² = .092, which was due to significantly more fixations during subordinate than during basic decisions for pools (basic: M = 2.52; subordinate: M = 3.91), t(26) = 1.901, p = .068, and for restaurants (basic: M = 3.01; subordinate: M = 4.69), t(26) = 3.363, p = .002.", 
    "For initial saccade latency, there was no main effect of judgment, F(1, 26) = 1.708, p = .203, ηp² = .062, or stimuli type, nor was there an interaction between the two for initial saccade latency (Fs < 1).", 
    "Fixation durations showed no main effect of judgment (F < 1), though there was an effect of stimuli type, F(2.288, 59.487) = 4.539, p = .011, ηp² = .149, (Ms = 257, 312, 265, and 277 ms for classrooms, pools, restaurants, and roads, respectively).", 
    "There was no interaction, F(3, 78) = 1.276, p = .288, ηp² = .047.", 
    "No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094.", 
    "No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094.", 
    "No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094.", 
    "No main effect of saccade amplitude on judgment appeared, F(1, 26) = 1.122, p = .299, ηp² = .041, but there was an effect of stimuli type, F(3, 78) = 20.836, p < .001, ηp² = .445 (Ms = 4.06°, 3.33°, 4.31°, and 3.44° for classrooms, pools, restaurants, and roads, respectively), and an interaction, F(3, 78) = 4.869, p = .004, ηp² = .158, with restaurants having a trend for longer saccades during subordinate categorizations (M = 4.62°) than during basic categorizations (M = 3.99°), t(26) = 1.735, p = .094."
    )), row.names = c(NA, -39L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c("5em", NA), 2, FALSE)
```

This will catch most comparators like =<>~≈≠≤≥≪≫ and most versions of scientific notation like 5.0 x 10^-2 or 5.0e-2. If you find any formats that are not correctly handled by this function, please contact debruine@gmail.com.

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

List all p-values in the text, returning the matched text (e.g., 'p = 0.04') and document location in a table.

Note that this will not catch p-values reported like "the p-value is 0.03" because that results in a ton of false positives when papers discuss p-value thresholds. If you need to detect text like that, use `text_search()` function and a custom pattern like "\\bp(-| )?values?\\s+.{1,20}\\s+[0-9\\.]+"

This will catch most comparators like =<>~≈≠≤≥≪≫ and most versions of scientific notation like 5.0 x 10^-2 or 5.0e-2. If you find any formats that are not correctly handled by this function, please contact the author.

This module only checks p-values reported in the running text of the manuscript. It cannot (yet) process p-values reported only in tables.

This module was developed by Lisa DeBruine

:::

## Reference Modules

### ✅️ Reference Accuracy {#reference-accuracy .green}

We checked the 0 references that supplied a DOI against the record that DOI points to, and found 0 incoherent references to check for parsing errors or mistakes. 3 references had no DOI and could not be checked. Incoherent references are mostly PDF parsing errors (we are working on improving reference parsing). Adding a DOI to every reference that has one lets the other reference checks (retraction, PubPeer, and replication) run on them too.

<details><summary>View detailed feedback</summary><div>

### References without a DOI

These references have no DOI, so they could not be checked here, and they also cannot be checked by the other reference modules (retraction, PubPeer, and replication checks all rely on the DOI). We searched CrossRef for a matching DOI; where a confident match was found it is suggested below. We recommend adding a DOI to every reference that has one: it lets these checks run and makes each cited work easier to find and verify.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(Reference = c("Biederman, I. (1995). Visual object recognition. In S. F. Kosslyn & D. N. Osherson (Eds.), An invitation to cognitive science (2nd ed., Vol. 2, pp. 121-165). Cambridge, MA: MIT Press.", 
"Potter, M. C. (1975). Meaning in visual scenes. Science, 187, 965-966.", 
"Rosch, E. (1978). Principles of categorization. In E. Rosch & B. B. Lloyd (Eds.), Cognition and categorization (pp. 28- 48). Hillsdale, NJ: Erlbaum."
), "Suggested DOI" = c("", "", "")), row.names = c(NA, -3L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.7, 0.3), 5, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

This module checks whether each reference with a DOI is internally coherent: it compares the details the paper cites for a reference against the authoritative record that the reference's DOI points to, and flags any reference whose cited details do not match.

This module looks for *incoherent* references: a reference is incoherent when the title, authors, journal, or year that the paper cites disagree with the record that the reference's own DOI points to. Currently, it will most often be a parsing error where the reference list from the PDF is not extracted perfectly accurately, but the module can point out AI generated references, of mistakes in citations. You will need check the original source.

The module uses the `bib_match` table, which holds the metadata retrieved from CrossRef for each reference (added or refreshed with `add_bib_match()`, which makes live network calls).

**Only references that supply their own DOI are checked.** For these, we look up the record that exact DOI points to and compare it field by field against what the paper cites. A reference with no DOI is *not* checked: the only record we could find for it comes from a CrossRef title search, which often returns the wrong paper, so any "mismatch" would be CrossRef's error rather than the citation's. References without a DOI are instead listed separately, with a recommendation to add a DOI where one exists. For those, a suggested DOI is offered only when CrossRef found a high-confidence match (controlled by `suggest_score`).

For each checked reference we compare five fields against the DOI's record:

- **DOI** — flagged only when the reference printed a DOI that differs from the record (a blank cited DOI is never a mismatch).
- **Year** — flagged when the cited year is more than `year_tolerance` years from the record (online-first and print years routinely differ by one year, so this is allowed by default).
- **Journal** — flagged when the cited journal disagrees with the record. Journal names are matched tolerantly: standard ISO-4 abbreviations (e.g. "J. Pers. Soc. Psychol." for "Journal of Personality and Social Psychology"), "&"/"and", and "the" are treated as equivalent.
- **Title** — flagged when the cited title is too different from the record's title, judged by character-level similarity (`title_similarity`) after stripping case, punctuation, footnote markers and diacritics. This ignores cosmetic differences (colons, question marks, em-dash spacing, line-break word splits) while still catching a genuinely different title.
- **Authors** — flagged when the leading author surnames (the first `max_authors`) from the record are not all present in the cited author list. Only the leading authors are required because author lists are routinely truncated with "et al.". Diacritics are ignored, so "Gredebäck" and "Gredeback" match.

DOI, journal and year are reliable signals and flag a reference on their own. Title and author mismatches are more often caused by imperfect PDF parsing, so these are governed by `min_mismatches`: the default (1) flags a reference when either the title or the authors disagree. Set `min_mismatches = 2` to be more conservative and require both to disagree (fewer false positives, lower recall).

The report lists each incoherent reference with the specific cited value struck through and the record's value beside it, so the discrepancy is visible at a glance.

This module was developed by Daniel Lakens and Lisa DeBruine

:::

::: {.validation}
Validation: In validation on psychology references with a DOI, the module flagged genuine, coherent references at a low rate: around 8% of checked references at the default setting (min_mismatches = 1), and about 3% with the more conservative setting (min_mismatches = 2). On deliberately corrupted references it caught journal and year fabrications reliably (about 96-100%) at either setting, and essentially all single-field fabrications (including single title or author changes) at min_mismatches = 1. Importantly, in a hand-review of references flagged across 10 papers from 5 fields, the large majority of flags were imperfect extraction of the reference from the PDF (for example a journal name mis-parsed, or two references merged) rather than genuine citation errors. Real citation mistakes are rare, so even though the false positive rate is low, a flag should be read as "check this reference against the original source", not as a confirmed error.
:::

### ℹ️ Summarise References {#summarise-references .info}

Summary information provided for 26 references

<details><summary>View detailed feedback</summary><div>

See the specific reports above for details.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(text = c("Biederman, I. (1987). Recognition-by-components: A theory of human image understanding. Psychological Review, 94, 115-147.", 
"Biederman, I. (1995). Visual object recognition. In S. F. Kosslyn & D. N. Osherson (Eds.), An invitation to cognitive science (2nd ed., Vol. 2, pp. 121-165). Cambridge, MA: MIT Press.", 
"Delorme, A., Richard, G., & Fabre-Thorpe, M. (2000). Ultra- rapid categorisation of natural scenes does not rely on colour cues: A study in monkeys and humans. Vision Research, 40, 2187-2200.", 
"Fei-Fei, L., Iyer, A., Koch, C., & Perona, P. (2007). What do we perceive in a glance of a real-world scene? Journal of Vision, 7(1), Article 10. Retrieved from http://www .journalofvision.org/content/7/1/10", 
"Gosselin, F., & Schyns, P. G. (2001). Why do we SLIP to the basic level? Computational constraints and their implemen- tation. Psychological Review, 108, 735-758.", 
"Greene, M. R., & Oliva, A. (2009a). The briefest of glances: The time course of natural scene understanding. Psychological Science, 20, 464-472.", 
"Greene, M. R., & Oliva, A. (2009b). Recognition of natural scenes from global properties: Seeing the forest without representing the trees. Cognitive Psychology, 58, 137-179.", 
"Joubert, O., Rousselet, G., Fize, D., & Fabre-Thorpe, M. (2007). Processing scene context: Fast categoriza- tion and object interference. Vision Research, 47, 3286- 3297.", 
"Loschky, L. C., & Larson, A. M. (2010). The natural/man-made distinction is made prior to basic-level distinctions in scene gist processing. Visual Cognition, 18, 513-536.", 
"McConkie, G. W., & Rayner, K. (1975). The span of the effec- tive stimulus during a fixation in reading. Perception & Psychophysics, 17, 578-586.", 
"Oliva, A., & Schyns, P. (1997). Coarse blobs or fine edges? Evidence that information diagnosticity changes the per- ception of complex visual stimuli. Cognitive Psychology, 34, 72-107.", 
"Oliva, A., & Torralba, A. (2001). Modeling the shape of the scene: A holistic representation of the spatial enve- lope. International Journal of Computer Vision, 42, 145- 175.", 
"Oliva, A., & Torralba, A. (2006). Building the gist of a scene: The role of global image features in recognition. Progress in Brain Research: Visual Perception, 155, 23-36.", 
"Potter, M. C. (1975). Meaning in visual scenes. Science, 187, 965-966.", 
"Potter, M. C. (1976). Short-term conceptual memory for pictures. Journal of Experimental Psychology: Human Learning and Memory, 2, 509-522.", 
"Rosch, E. (1978). Principles of categorization. In E. Rosch & B. B. Lloyd (Eds.), Cognition and categorization (pp. 28- 48). Hillsdale, NJ: Erlbaum.", 
"Rosch, E., Mervis, C. B., Gray, W. D., Johnson, D. M., & Boyes- Braem, P. (1976). Basic objects in natural categories. Cognitive Psychology, 8, 382-439.", 
"Rotshtein, P., Schofield, A., Funes, M. J., & Humphreys, G. W. (2010). Effects of spatial frequency bands on perceptual decision: It is not the stimuli but the comparison. Journal of Vision, 10(10), Article 25. Retrieved from http://www .journalofvision.org/content/10/10/25.full", 
"Rousselet, G. A., Joubert, O. R., & Fabre-Thorpe, M. (2005). How long to get to the \"gist\" of real-world natural scenes? Visual Cognition, 12, 852-877.", 
"Schyns, P. G. (1998). Diagnostic recognition: Task constraints, object information, and their interactions. Cognition, 67, 147-179.", 
"Schyns, P. G., & Oliva, A. (1994). From blobs to boundary edges: Evidence for time-and spatial-scale-dependent scene recognition. Psychological Science, 5, 195-200.", 
"Serre, T., Oliva, A., & Poggio, T. (2007). A feedforward archi- tecture accounts for rapid categorization. Proceedings of the National Academy of Sciences, USA, 104, 6424-6429.", 
"Thorpe, S. J., Fize, D., & Marlot, C. (1996). Speed of processing in the human visual system. Nature, 381, 520-522.", 
"Torralba, A., & Oliva, A. (2003). Statistics of natural image categories. Network: Computation in Neural Systems, 14, 391-412.", 
"Tversky, B., & Hemenway, K. (1983). Categories of environ- mental scenes. Cognitive Psychology, 15, 121-149.", 
"VanRullen, R., & Thorpe, S. J. (2002). Surfing a spike wave down the ventral stream. Vision Research, 42, 2593-2615."
), accuracy_mismatch = c(NA_character_, NA_character_, NA_character_, 
NA_character_, NA_character_, NA_character_, NA_character_, NA_character_, 
NA_character_, NA_character_, NA_character_, NA_character_, NA_character_, 
NA_character_, NA_character_, NA_character_, NA_character_, NA_character_, 
NA_character_, NA_character_, NA_character_, NA_character_, NA_character_, 
NA_character_, NA_character_, NA_character_)), row.names = c(NA, 
-26L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, c(0.75, NA), 10, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Summarise information about each reference in a paper.

This module summarises previously-run reference section modules: ref_accuracy, ref_pubpeer, ref_replication, and ref_retraction.

This module was developed by Lisa DeBruine

:::

### ⚠️ Reference Consistency {#reference-consistency .red}

There are cross-references that are not in the bibliography and/or bibliography entries not cross-referenced in the text

<details><summary>View detailed feedback</summary><div>

This module relies on Grobid correctly parsing the references. There are likley to be some false positives.

```{r}
#| echo: false

# table data --------------------------------------
table <- structure(list(bib_id = c(6L, NA, NA), type = c("extra", "missing", 
"missing"), contents = c(NA, ", 2009b;", "(Greene & Oliva, 2009b;"
), reference = c("Greene, M. R., & Oliva, A. (2009b). Recognition of natural scenes from global properties: Seeing the forest without representing the trees. Cognitive Psychology, 58, 137-179.", 
"These incredible scene-processing speeds have often led researchers to treat categorization as a perceptually driven process with semantic meaning passively emerging in a set hierarchy as critical properties become available to the visual system (Fei-Fei, Iyer, Koch, & Perona, 2007;Greene & Oliva, 2009a, 2009b;Joubert, Rousselet, Fize, & Fabre-Thorpe, 2007;Loschky & Larson, 2010;Oliva & Torralba, 2001;Rousselet, Joubert, & Fabre-Thorpe, 2005;Schyns & Oliva, 1994;Torralba & Oliva, 2003), perhaps as a result of a feed-forward network (Delorme, Richard, & Fabre-Thorpe, 2000;Serre, Oliva, & Poggio, 2007;Thorpe, Fize, & Marlot, 1996;VanRullen & Thorpe, 2002).", 
"Several candidates have emerged, such as the spatial regularities between volumetric forms (Biederman,1987(Biederman, , 1995) ) or the variety of simple image statistics at low spatial resolutions (Greene & Oliva, 2009b;Oliva & Torralba,2001, 2006;Schyns & Oliva, 1994)."
)), row.names = c(NA, -3L), class = "data.frame")

# display table -----------------------------------
metacheck::report_table(table, "auto", 2, FALSE)
```

</div></details>

::: {.callout-note title="How It Works" collapse="true"}

Check if all references are cited and all citations are referenced

This module is currently under development and should not be relied on until we have increased the accuracy of the reference labeling while importing papers. It has a high false-positive rate because grobid (the PDF-importing tool) tends to miss some references and falsely identify some text as citations.

This module was developed by Lisa DeBruine

:::

### ✅️ Miscitation {#miscitation .green}

We detected no miscited papers

::: {.callout-note title="How It Works" collapse="true"}

Check for frequently miscited papers. This module is just a proof of concept -- the miscite database is not yet populated with real examples.

If you want to use your own database, create a data frame with the columns "doi", "reftext", and "warning", which will be used to match the DOI in papers (use short DOIs like xxx/1234, not https://doi.org/xxx/1234) and produce the report text.

This module was developed by Lisa DeBruine

:::




